---
title: "Scorecard Update"
author: "Erik Larsen"
date: "`r Sys.Date()`"
output: 
  html_document:
    self-contained: no
    code_folding: hide
    toc: TRUE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
    fig_caption: TRUE
---

# Environment {.tabset .tabset-fade .tabset-pills}

## Attach Packages

```{r setup, include = F, message = F, warning = F, echo = F, eval = T}
knitr::opts_chunk$set(echo = FALSE) 
```

```{r Attach Packages, include = T, message = F, warning = F, eval = T}
library(golf)
library(tidyverse)
library(lme4)
library(mgcv)
library(brms)
library(DBI)
library(RSQLite)
# library(blastula)
# library(keyring)
# library(mailR)
library(emayili)
```

## Connect to the db

```{r Connect to the db, include = T, message = F, warning = F, eval = T}
con <- RSQLite::dbConnect(drv = RSQLite::SQLite(), dbname = 'golf_data')
```

# Record New Scorecard {.tabset .tabset-pills .tabset-fade}

## Input the Data

```{r Annotate the new data, include = T, message = F, warning = F, eval = T}
round_course <- 'Silverbell'
round_date <- '2026-01-18'
round_tees <- 'white'
hole_scores <- c(4, 6, 4, 4, 6, 4, 5, 6, 3,
                 5, 6, 6, 5, 5, 4, 4, 5, 5)
FIRs <- c(0, 0, 0, 1, 1, 0, 0, 0, 0,
          1, 0, 0, 0, 1, 0, 0, 0, 1)
GIRs <- c(0, 0, 0, 1, 0, 1, 1, 0, 1,
          1, 0, 0, 0, 1, 0, 0, 0, 0)
putts_rec <- c(1, 2, 1, 2, 2, 3, 2, 2, 2,
               3, 2, 3, 2, 3, 1, 2, 1, 1)
chips_rec <- c(1, 0, 1, 0, 2, 0, 0, 0, 0,
               0, 2, 2, 1, 0, 1, 1, 0, 1)
penalties_rec <- c(rep(0, 18))
tee_clubs <- c('4', 'D', 'GW', 'D', 'D', '7', 'D', '4', '8',
               'D', '4', '9', 'D', 'D', 'D', '5', '4', 'D')
index <- 10.2
```

## Get Metrics

```{r Specify the Course and Tees, include = T, message = F, warning = F, eval = T}
if ( length(hole_scores) > 0 ) {
 Card <- golf::getCourse(course = round_course, date = round_date, tees = round_tees) 
}
```

```{r Get Metrics, include = T, message = F, warning = F, eval = T}
if ( length(hole_scores) > 0 ) {
 Card <- golf::logScore(Scorecard = Card,
                       hole_by_hole = hole_scores,
                       GHIN = '10526424',
                       index = index,
                       FIR = FIRs,
                       GIR = GIRs,
                       putts = putts_rec,
                       chips = chips_rec,
                       penalties = penalties_rec,
                       tee_club = tee_clubs) 
}
```

# Update db {.tabset .tabset-pills .tabset-fade}

Update the db if the new round hasn't been logged yet

## Players Table

```{r Update the players table of the db, include = T, message = F, warning = F, eval = T}
if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM rounds ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &
     
     length(hole_scores) > 0
     ) {

  DBI::dbAppendTable(conn = con,
                   name = 'players',
                   value = players <- Card |> 
                     dplyr::select(GHIN, index, date) |> 
                     dplyr::distinct() |> 
                     dplyr::rename(handicap_index = index)
                   )
  
}
```

## Courses Table

```{r Update the courses table of the db, include = T, message = F, warning= F, eval = T}
if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM rounds ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &
     
     length(hole_scores) > 0
     ) {
  DBI::dbAppendTable(conn = con,
                   name = 'courses',
                   value = course <- Card |> 
                     dplyr::select(course, tees, to_par, slope, course_rating, hole, yds, par, hole_handicap) |> 
                     dplyr::distinct() |> 
                     dplyr::rename(course_name = course)
                   )
}
```

## Rounds Table

```{r Update the rounds table of the db, include= T, message = F, warning = F, eval = T}
if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM rounds ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &
     
     length(hole_scores) > 0
     ) {
  DBI::dbAppendTable(conn = con,
                   name = 'rounds',
                   value = round <- Card |> 
                     dplyr::select(c(GHIN:tees),c(hole,hole_handicap:tee_club)) |> 
                     dplyr::distinct() |> 
                     dplyr::rename(handicap_index = index, course_name = course)
                   )
}
```


```{r Clear Environment, include = T, message = F, warning = F, eval = T}
rm(list = ls()[which(grepl(ls(), pattern= 'con|round_course|round_date|index')==F)])
```

# Summarize Metrics {.tabset .tabset-pills .tabset-fade}

## Gather and Format

Gather and format from the database

```{r Summarize Metrics, include = T, message = F, warning = F, echo = T, eval = T}
scores <- DBI::dbGetQuery(conn = con, statement = paste0(
  "SELECT DISTINCT sub.* FROM
  (SELECT DISTINCT r.*, c.par, c.course_rating FROM rounds r
  LEFT JOIN courses c
  ON c.tees = r.tees
  AND c.course_name = r.course_name
  AND c.hole = r.hole
  AND c.hole_handicap = r.hole_handicap) AS sub
  INNER JOIN players p
  ON sub.GHIN = p.GHIN
  AND sub.handicap_index = p.handicap_index
  AND sub.date = p.date;"
)) |> 
  dplyr::mutate(date = lubridate::as_date(date),
                hole = stringr::str_extract(hole, pattern = '[0-9]{1,}') |> 
                  as.numeric()) |> 
  dplyr::relocate(par, .after = hole) |> 
  dplyr::relocate(course_rating, .after = tees) |>
  dplyr::group_by(date) |> 
  dplyr::arrange(desc(date), hole) |> 
  dplyr::ungroup()
```

## Compute Advanced Metrics

Compute more nuanced metrics

```{r Compute Advanced Metrics 1, include = T, warning = F, message = F, eval = T}
scores_sum <- scores |>
  dplyr::mutate(date_course = paste0(date,
                                     '\n',
                                     course_name, '\n',
                                     handicap_index),
                chips = dplyr::case_when(
                  grepl(date, pattern = '07-13') ~ NA_real_, TRUE ~ chips),
                `chips+putts` = chips+putts,
                FIR_opps = dplyr::case_when(par > 3 ~ 1, TRUE ~ NA),
                `Iron FIRs` = dplyr::case_when(par > 3 &
                                                 grepl(tee_club, pattern = '4|5') &
                                                 FIR == 1 ~ 1,
                                               TRUE ~ 0),
                `Iron FIR opps` = dplyr::case_when(par > 3 &
                                                     grepl(tee_club, pattern = '4|5') ~ 1,
                                                   TRUE ~ 0),
                `Driver FIRs` = dplyr::case_when(par > 3 &
                                                   tee_club == 'D' &
                                                   FIR == 1 ~ 1,
                                                 TRUE ~ 0),
                `Driver FIR opps` = dplyr::case_when(par > 3 &
                                                     tee_club == 'D' ~ 1,
                                                   TRUE ~ 0),
                `Par 3 GIRs` = dplyr::case_when(par == 3 & 
                                                  GIR == 1 ~ 1,
                                                TRUE ~ 0),
                greenie_putts = dplyr::case_when(GIR == 1 ~ putts, TRUE ~ NA_real_),
                updown_conv = dplyr::case_when(GIR == 0 &
                                                 par == gross ~ 1,
                                               TRUE ~ 0),
                updown_opps = dplyr::case_when(GIR == 0 &
                                                chips > 0 ~ 1,
                                              TRUE ~ 0)
                ) |> 
  dplyr::rename(`Handicap Index` = handicap_index) |> 
  dplyr::group_by(date, date_course, course_rating, `Handicap Index`) |> 
  dplyr::summarize(
                   FIRs = sum(FIR, na.rm = F),
                   `Iron FIRs` = sum(`Iron FIRs`, na.rm = T),
                   `Iron FIR%` = round(((sum(`Iron FIRs`, na.rm = T)/sum(`Iron FIR opps`, na.rm = T))*100), 1),
                   `Driver FIRs` = sum(`Driver FIRs`, na.rm = T),
                   `Driver FIR%` = round(((sum(`Driver FIRs`, na.rm = T)/sum(`Driver FIR opps`, na.rm = T))*100), 1),
                   `FIR%` = round((sum(FIRs, na.rm = T)/sum(FIR_opps, na.rm = T))*100, 1),
                   GIRs = sum(GIR, na.rm = F),
                   `Par 3 GIRs` = sum(`Par 3 GIRs`, na.rm = T),
                   `GIR%` = round((sum(GIRs, na.rm = T)/18)*100, 1),
                   putts = sum(putts, na.rm = F),
                   `Avg GIR putts` = round(mean(greenie_putts, na.rm = T), 2),
                   chips = sum(chips, na.rm = F),
                   `chips+putts` = sum(`chips+putts`, na.rm = F),
                   `UpDown%` = round(((sum(updown_conv, na.rm = T)/sum(updown_opps, na.rm = T))*100), 1),
                   pars = sum(is_gross_par, na.rm = F),
                   birdies = sum(is_gross_birdie, na.rm = F),
                   bogies = sum(is_gross_bogey, na.rm = F),
                   `doubles+` = sum(is_gross_bogey_worse, na.rm = F),
                   penalties = sum(penalties, na.rm = T),
                   `Gross Score` = mean(tot_gross, na.rm = F),
                   `Net Score` = mean(tot_net, na.rm = F)) %>%
  dplyr::mutate(dplyr::across(c(`Iron FIRs`, `Driver FIRs`, `Iron FIR%`, `Driver FIR%`, `FIR%`), ~dplyr::if_else(is.na(FIRs), NA, .)),
                dplyr::across(c(`Par 3 GIRs`, `Avg GIR putts`, `UpDown%`, `GIR%`), ~dplyr::if_else(is.na(GIRs), NA, .)),
                `chips+putts` = dplyr::case_when(is.na(chips) ~ NA_real_,
                                                 TRUE ~ `chips+putts`)) %>% 
  dplyr::mutate(`UpAndDown%` = dplyr::case_when(grepl(date, pattern = '07-13|09-21') ~ NA, TRUE ~ `UpDown%`),
                `Iron FIR%` = dplyr::case_when(`Iron FIR%` == NaN ~ 0.0, TRUE ~ `Iron FIR%`))
```

```{r Compute Advanced Metrics 2, include = T, warning = F, message = F, eval = T}
head(scores_sum)
```

## Separate Metrics {.tabset .tabset-pills .tabset-fade}

Separate the metrics:

### Scoring Metrics

Scores and Handicap

```{r Separate By Type 1, include = T, warning = F, message = F, eval = T}
scoring_metrics <- scores_sum |> 
  dplyr::select(`Handicap Index`, `Gross Score`, `Net Score`)
head(scoring_metrics)
```

### Stroke Metrics

Pars, birdies, bogies, etc.

```{r Separate By Type 2, include = T, warning = F, message = F, eval = T}
stroke_metrics <- scores_sum |> 
  dplyr::select(`doubles+`, bogies, pars, birdies)
head(stroke_metrics)
```

### Around-the-Green Metrics

Chips, putts, etc.

```{r Separate By Type 3, include = T, warning = F, message = F, eval = T}
atg_metrics <- scores_sum |> 
  dplyr::select(chips, `chips+putts`, `UpAndDown%`, putts, `Avg GIR putts`)
head(atg_metrics)
```

### Ball Striking Metrics

Approach and tee accuracy

```{r Separate By Type 4, include = T, warning = F, message = F, eval = T}
ball_striking_metrics <- scores_sum |> 
  dplyr::select(GIRs, `GIR%`, `Par 3 GIRs`,
                FIRs, `FIR%`, `Iron FIRs`, `Iron FIR%`,
                `Driver FIRs`, `Driver FIR%`)
head(ball_striking_metrics)
```

# Plot Metrics {.tabset .tabset-pills .tabset-fade}

## Scoring Metrics

```{r Plot Scoring Metrics, include = T, message = F, warning = F, eval = T}
scoring_metrics |> 
  dplyr::mutate(course_rating = dplyr::case_when(grepl(date_course, pattern = 'Sewailo') ~ 68.9, TRUE ~ course_rating),
                `Handicap Index` = `Handicap Index`*4.5) |>
  dplyr::rename(`Course Rating` = course_rating) |> 
  dplyr::group_by(date, date_course, `Handicap Index`) |> 
  tidyr::pivot_longer(cols = c(`Course Rating`:`Net Score`), names_to = 'metric', values_to = 'value', values_drop_na = F) |> 
  ggplot2::ggplot(aes(x = date_course, y = value)) +
  ggplot2::geom_point(aes(x = date, y = value, size = 4, alpha = 0.1,
                          color = factor(metric,
                                         levels = c('Handicap Index', 'Course Rating', 'Gross Score', 'Net Score')),
                          fill = factor(metric,
                                         levels = c('Handicap Index', 'Course Rating', 'Gross Score', 'Net Score')))) +
  ggplot2::geom_line(aes(x = date, y = value, size = 1, alpha = 0.1,
                          color = factor(metric,
                                         levels = c('Handicap Index', 'Course Rating', 'Gross Score', 'Net Score')),
                          fill = factor(metric,
                                         levels = c('Handicap Index', 'Course Rating', 'Gross Score', 'Net Score')))) +
  ggplot2::geom_smooth(aes(x = date, y = value, group = metric,
                           color = factor(metric,
                                          levels = c('Handicap Index', 'Course Rating', 'Gross Score', 'Net Score')),
                           fill = factor(metric,
                                         levels = c('Handicap Index', 'Course Rating', 'Gross Score', 'Net Score'))),
                       alpha = 0.3, method = 'lm') +
  ggplot2::scale_y_continuous(sec.axis = ggplot2::sec_axis(~./4.5, name = 'Handicap Index'))+
  ggplot2::labs(title = paste0('Performance Over Time\n',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::last() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character(),
                               ' - ',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::first() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character()),
                x = 'date',
                y = 'metric',
                color = 'metric'
                ) +
  ggplot2::guides(alpha = 'none', size = 'none', fill = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(panel.grid.minor = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(face = 'bold'),
                 axis.text.y = ggplot2::element_text(face = 'bold'),
                 axis.text.x = ggplot2::element_text(face = 'bold', angle = 0, hjust = 0, vjust = 0),
                 title = ggplot2::element_text(face = 'bold')
                 ) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b')
```


## Stroke Metrics

```{r Plot Stroke Metrics, include = T, message = F, warning = F, eval = T}
stroke_metrics |> 
  tidyr::pivot_longer(cols = c(`doubles+`:birdies), names_to = 'metric', values_to = 'value', values_drop_na = F) |> 
  ggplot2::ggplot(aes(x = date_course, y = value, group = metric, color = metric, fill = metric)) +
  ggplot2::geom_point(aes(x = date, y = value, size = 4, alpha = 0.1), na.rm = T) +
  ggplot2::geom_line(aes(x = date, y = value, size = 1, alpha = 0.1), na.rm = T) +
  ggplot2::geom_smooth(aes(x = date, y = value), alpha = 0.3, method = 'lm') +
  ggplot2::labs(title = paste0('Hole-by-Hole Scores Over Time\n',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::last() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character(),
                               ' - ',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::first() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character()),
                x = 'date',
                y = 'metric',
                color = 'metric', fill = 'metric') +
  ggplot2::guides(alpha = 'none', size = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = 'none',
                 panel.grid.minor = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(face = 'bold'),
                 axis.text.y = ggplot2::element_text(face = 'bold'),
                 axis.text.x = ggplot2::element_text(face = 'bold', angle = 270, hjust = 0, vjust = 0.5),
                 title = ggplot2::element_text(face = 'bold'),
                 strip.text.x.top = ggplot2::element_text(face = 'bold')) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b') +
  ggplot2::facet_wrap(~factor(metric, levels = c('doubles+', 'bogies', 'pars', 'birdies')), nrow = 1)
```

## Around the Green Metrics

```{r Plot Around the Green Metrics, include = T, message = F, warning = F, eval = T}
atg_metrics |> 
  tidyr::pivot_longer(cols = c(chips:`Avg GIR putts`), names_to = 'metric', values_to = 'value', values_drop_na = F) |> 
  ggplot2::ggplot(aes(x = date_course, y = value, group = metric, color = metric, fill = metric)) +
  ggplot2::geom_point(aes(x = date, y = value, size = 4, alpha = 0.1), na.rm = T) +
  ggplot2::geom_line(aes(x = date, y = value, size = 1, alpha = 0.1), na.rm = T) +
  ggplot2::geom_smooth(aes(x = date, y = value), alpha = 0.3, method = 'lm') +
  ggplot2::labs(title = paste0('Around the Green Metrics Over Time\n',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::last() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character(),
                               ' - ',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::first() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character()),
                x = 'date',
                y = 'metric',
                color = 'metric', fill = 'metric') +
  ggplot2::guides(alpha = 'none', size = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = 'none',
                 panel.grid.minor = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(face = 'bold'),
                 axis.text.y = ggplot2::element_text(face = 'bold'),
                 axis.text.x = ggplot2::element_text(face = 'bold', angle = 270, hjust = 0, vjust = 0.5),
                 title = ggplot2::element_text(face = 'bold'),
                 strip.text.x.top = ggplot2::element_text(face = 'bold')) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b') +
  ggplot2::facet_wrap(~factor(metric, levels = c('chips', 'chips+putts', 'UpAndDown%', 'putts', 'Avg GIR putts')), scales = 'free')
```

## Ball Striking Metrics

```{r Plot Ball Striking Metrics, include = T, message = F, warning = F, eval = T, fig.width=8, fig.height = 8}
ball_striking_metrics |> 
  tidyr::pivot_longer(cols = c(GIRs:`Driver FIR%`), names_to = 'metric', values_to = 'value', values_drop_na = F) |> 
  ggplot2::ggplot(aes(x = date_course, y = value, group = metric, color = metric, fill = metric)) +
  ggplot2::geom_point(aes(x = date, y = value, size = 4, alpha = 0.1), na.rm = T) +
  ggplot2::geom_line(aes(x = date, y = value, size = 1, alpha = 0.1), na.rm = T) +
  ggplot2::geom_smooth(aes(x = date, y = value), alpha = 0.3, method = 'lm') +
  ggplot2::labs(title = paste0('Ball Striking Over Time\n',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::last() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character(),
                               ' - ',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::first() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character()),
                x = 'date',
                y = 'metric',
                color = 'metric', fill = 'metric') +
  ggplot2::guides(alpha = 'none', size = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = 'none',
                 panel.grid.minor = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(face = 'bold'),
                 axis.text.y = ggplot2::element_text(face = 'bold'),
                 axis.text.x = ggplot2::element_text(face = 'bold', angle = 270, hjust = 0, vjust = 0.5),
                 title = ggplot2::element_text(face = 'bold'),
                 strip.text.x.top = ggplot2::element_text(face = 'bold')) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b') +
  ggplot2::facet_wrap(~factor(metric,levels = c('Driver FIRs', 'Iron FIRs', 'FIRs',
                                                'Driver FIR%', 'Iron FIR%', 'FIR%',
                                                'GIRs', 'Par 3 GIRs', 'GIR%')), scales = 'free')
```

## Main Metrics

```{r Plot Main Metrics, include = T, message = F, warning = F, eval = T, fig.height=12, fig.width=10}
scores_sum |> 
  dplyr::mutate(course_rating = dplyr::case_when(grepl(date_course, pattern = 'Sewailo') ~ 68.9, TRUE ~ course_rating)) |> 
  tidyr::pivot_longer(cols = c(`Handicap Index`, `Gross Score`, `Net Score`,
                               `doubles+`, bogies, pars, birdies, chips, putts,
                               `UpDown%`,`Avg GIR putts`, `GIR%`, `Par 3 GIRs`,
                               `Iron FIR%`, `Driver FIR%`), names_to = 'metric', values_to = 'value', values_drop_na = F) |> 
  ggplot2::ggplot(aes(x = date_course, y = value, group = metric, color = metric, fill = metric)) +
  ggplot2::geom_point(aes(x = date, y = value, size = 4, alpha = 0.1), na.rm = T) +
  ggplot2::geom_line(aes(x = date, y = value, size = 1, alpha = 0.1), na.rm = T) +
  ggplot2::geom_smooth(aes(x = date, y = value), alpha = 0.3, method = 'lm') +
  ggplot2::labs(title = paste0('Performance Over Time\n',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::last() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character(),
                               ' - ',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::first() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character()),
                x = 'date',
                y = 'metric',
                color = 'metric', fill = 'metric') +
  ggplot2::guides(alpha = 'none', size = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = 'none',
                 panel.grid.minor = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(face = 'bold'),
                 axis.text.y = ggplot2::element_text(face = 'bold'),
                 axis.text.x = ggplot2::element_text(face = 'bold', angle = 270, hjust = 0, vjust = 0.5),
                 title = ggplot2::element_text(face = 'bold'),
                 strip.text.x.top = ggplot2::element_text(face = 'bold')) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b') +
  ggplot2::facet_wrap(~factor(metric,
                      levels = c('Handicap Index', 'Gross Score', 'Net Score',
                                 'doubles+', 'bogies', 'pars', 'birdies',
                                 'chips', 'putts', 'UpDown%', 'Avg GIR putts',
                                 'GIR%', 'Par 3 GIRs', 'Iron FIR%', 'Driver FIR%')),
                      scales = 'free',
                      ncol = 4)
```


```{r Disconnect from the DB, include = T, message = F, warning = F, echo = F, eval = T}
DBI::dbDisconnect(conn = con)
```

