---
title: "Predicting Gross Scores"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Predicting Gross Scores}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 10,
  dev = c("png", "pdf"),
  fig.path = "../inst/figures/LMER_predictions/"
)
```

```{r db-isolation, include=FALSE}
# Create a disposable copy of the production DB for vignette execution
tmp_db <- tempfile(fileext = ".db")
file.copy(system.file("extdata", "golf_data.db", package = "golf"), tmp_db, overwrite = TRUE)

# Override the package's DB path for the vignette
db_path <- tmp_db
```


# Overview

This vignette shows the linear mixed model used to measure my performance for each golf round and use that information to predict my performance for the next golf round

Please see [this article for a more detailed version](../inst/articles/predict_score.html) explaining golf and model jargon

```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('# Environment {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>Environment</strong></summary>\n')
} else {
  cat('# Environment\n')
}
```

## Attach Packages

```{r Attach Packages, include = T, message = F, warning = F, echo = T}
library(golf)
library(tidyverse)
library(lme4)
library(mgcv)
library(brms)
library(DBI)
library(RSQLite)
library(emayili)
```

```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('# Summarize Metrics {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>Summarize Metrics</strong></summary>\n')
} else {
  cat('# Summarize Metrics\n')
}
```

## Gather and Format

Gather and format from the database

```{r Summarize Metrics, include = T, message = F, warning = F, echo = T, echo = T}
## connect to the db
con <- golf::get_db_connection(db_path = db_path)

scores <- DBI::dbGetQuery(conn = con, statement = paste0(
  "SELECT DISTINCT sub.* FROM
  (SELECT DISTINCT r.*, c.par, c.course_rating FROM rounds r
  LEFT JOIN courses c
  ON c.tees = r.tees
  AND c.course_name = r.course_name
  AND c.hole = r.hole
  AND c.hole_handicap = r.hole_handicap) AS sub
  INNER JOIN players p
  ON sub.GHIN = p.GHIN
  AND sub.handicap_index = p.handicap_index
  AND sub.date = p.date;"
)) |> 
  dplyr::mutate(date = lubridate::as_date(date),
                hole = stringr::str_extract(hole, pattern = '[0-9]{1,}') |> 
                  as.numeric()) |> 
  dplyr::relocate(par, .after = hole) |> 
  dplyr::relocate(course_rating, .after = tees) |>
  dplyr::group_by(date) |> 
  dplyr::arrange(desc(date), hole) |> 
  dplyr::ungroup()
```

## Compute Advanced Metrics

Compute more nuanced metrics

```{r Compute Advanced Metrics 1, include = T, warning = F, message = F, echo = F}
scores_sum <- scores |>
  dplyr::mutate(date_course = paste0(date,
                                     '\n',
                                     course_name, '\n',
                                     handicap_index),
                chips = dplyr::case_when(
                  grepl(date, pattern = '07-13') ~ NA_real_, TRUE ~ chips),
                `chips+putts` = chips+putts,
                FIR_opps = dplyr::case_when(par > 3 ~ 1, TRUE ~ NA),
                `Iron FIRs` = dplyr::case_when(par > 3 &
                                                 grepl(tee_club, pattern = '4|5') &
                                                 FIR == 1 ~ 1,
                                               TRUE ~ 0),
                `Iron FIR opps` = dplyr::case_when(par > 3 &
                                                     grepl(tee_club, pattern = '4|5') ~ 1,
                                                   TRUE ~ 0),
                `Driver FIRs` = dplyr::case_when(par > 3 &
                                                   tee_club == 'D' &
                                                   FIR == 1 ~ 1,
                                                 TRUE ~ 0),
                `Driver FIR opps` = dplyr::case_when(par > 3 &
                                                     tee_club == 'D' ~ 1,
                                                   TRUE ~ 0),
                `Par 3 GIRs` = dplyr::case_when(par == 3 & 
                                                  GIR == 1 ~ 1,
                                                TRUE ~ 0),
                greenie_putts = dplyr::case_when(GIR == 1 ~ putts, TRUE ~ NA_real_),
                updown_conv = dplyr::case_when(GIR == 0 &
                                                 par == gross ~ 1,
                                               TRUE ~ 0),
                updown_opps = dplyr::case_when(GIR == 0 &
                                                chips > 0 ~ 1,
                                              TRUE ~ 0)
                ) |> 
  dplyr::rename(`Handicap Index` = handicap_index) |> 
  dplyr::group_by(GHIN, date, date_course, course_rating, `Handicap Index`) |> 
  dplyr::summarize(
                   FIRs = sum(FIR, na.rm = F),
                   `Iron FIRs` = sum(`Iron FIRs`, na.rm = T),
                   `Iron FIR%` = round(((sum(`Iron FIRs`, na.rm = T)/sum(`Iron FIR opps`, na.rm = T))*100), 1),
                   `Driver FIRs` = sum(`Driver FIRs`, na.rm = T),
                   `Driver FIR%` = round(((sum(`Driver FIRs`, na.rm = T)/sum(`Driver FIR opps`, na.rm = T))*100), 1),
                   `FIR%` = round((sum(FIRs, na.rm = T)/sum(FIR_opps, na.rm = T))*100, 1),
                   GIRs = sum(GIR, na.rm = F),
                   `Par 3 GIRs` = sum(`Par 3 GIRs`, na.rm = T),
                   `GIR%` = round((sum(GIRs, na.rm = T)/18)*100, 1),
                   putts = sum(putts, na.rm = F),
                   `Avg GIR putts` = round(mean(greenie_putts, na.rm = T), 2),
                   chips = sum(chips, na.rm = F),
                   `chips+putts` = sum(`chips+putts`, na.rm = F),
                   `UpDown%` = round(((sum(updown_conv, na.rm = T)/sum(updown_opps, na.rm = T))*100), 1),
                   pars = sum(is_gross_par, na.rm = F),
                   birdies = sum(is_gross_birdie, na.rm = F),
                   bogies = sum(is_gross_bogey, na.rm = F),
                   `doubles+` = sum(is_gross_bogey_worse, na.rm = F),
                   penalties = sum(penalties, na.rm = T),
                   `Gross Score` = mean(tot_gross, na.rm = F),
                   `Net Score` = mean(tot_net, na.rm = F)) %>%
  dplyr::mutate(dplyr::across(c(`Iron FIRs`, `Driver FIRs`, `Iron FIR%`, `Driver FIR%`, `FIR%`), ~dplyr::if_else(is.na(FIRs), NA, .)),
                dplyr::across(c(`Par 3 GIRs`, `Avg GIR putts`, `UpDown%`, `GIR%`), ~dplyr::if_else(is.na(GIRs), NA, .)),
                `chips+putts` = dplyr::case_when(is.na(chips) ~ NA_real_,
                                                 TRUE ~ `chips+putts`)) %>% 
  dplyr::mutate(`UpDown%` = dplyr::case_when(grepl(date, pattern = '07-13|09-21') ~ NA, TRUE ~ `UpDown%`),
                `Iron FIR%` = dplyr::case_when(`Iron FIR%` == NaN ~ 0.0, TRUE ~ `Iron FIR%`))
```

```{r Compute Advanced Metrics 2, include = T, warning = F, message = F, echo = T}
head(scores_sum |> 
       dplyr::arrange(desc(date)))
```

```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('## Separate Metrics {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>Separate Metrics</strong></summary>\n')
} else {
  cat('## Separate Metrics\n')
}
```

Separate the metrics:

### Scoring Metrics

Round scores and `Handicap Index`

```{r Separate By Type 1, include = T, warning = F, message = F, echo = T}
scoring_metrics <- scores_sum |> 
  dplyr::select(`Handicap Index`, `Gross Score`, `Net Score`)
head(scoring_metrics |> 
       dplyr::arrange(desc(date)))
```

### Stroke Metrics

Above/below par

```{r Separate By Type 2, include = T, warning = F, message = F, echo = T}
stroke_metrics <- scores_sum |> 
  dplyr::select(`doubles+`, bogies, pars, birdies)
head(stroke_metrics |> 
       dplyr::arrange(desc(date)))
```

### Around-the-Green Metrics

Chips, putts, etc.

```{r Separate By Type 3, include = T, warning = F, message = F, echo = T}
atg_metrics <- scores_sum |> 
  dplyr::select(chips, `chips+putts`, `UpDown%`, putts, `Avg GIR putts`)
head(atg_metrics |> 
       dplyr::arrange(desc(date)))
```

### Ball Striking

Approach and tee accuracy

```{r Separate By Type 4, include = T, warning = F, message = F, echo = T}
ball_striking_metrics <- scores_sum |> 
  dplyr::select(GIRs, `GIR%`, `Par 3 GIRs`,
                FIRs, `FIR%`, `Iron FIRs`, `Iron FIR%`,
                `Driver FIRs`, `Driver FIR%`)
head(ball_striking_metrics |> 
       dplyr::arrange(desc(date)))
```

```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('# LMER Model {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>LMER Model</strong></summary>\n')
} else {
  cat('# LMER Model\n')
}
```

## Fit LMER

Fit a lmer model to the data to capture repeated measurements of `Gross Score` 
predicted by `Handicap Index` and `course_rating`

```{r Fit the model, include = T, message = F, warning = F, echo = T}
# Fit a model to the data

gross_lmer <- lme4::lmer(
  
  data = scores_sum |> 
    dplyr::ungroup() |> 
    dplyr::mutate(
      
      course_rating = mean(course_rating) - course_rating, 
      
      course = gsub(date_course,
                    pattern = '[0-9]|\\-|\\\n|\\.',
                    replacement = ''), # extract the course names
      
      `Handicap Index` = mean(`Handicap Index`) - `Handicap Index`,
      days = as.numeric(date - min(date) + 1,
                        units = 'days')
      ) |> # create a 'days' metric starting at the first day joining the club 
    
    dplyr::relocate(days, .after = date),
  
  formula = 
    `Gross Score` ~
    `Handicap Index` +
    course_rating +
    course + 
    days +
    (1 + `Handicap Index`|course) + # random intercepts and random slopes for Gross Score at a course given a Handicap Index
    (1 + `Handicap Index`|course_rating) # random intercepts and random slopes for Gross Score at a course rating given a Handicap Index
           )
```

## LMER Model Summary

```{r Show Model results, include = T, message = F, warning = F, eval = T, echo = F}
summary(gross_lmer)
```
```{r Extract RE, include = T, message = F, warning = F, eval = T, echo = F}
vc_df <- gross_lmer |> 
  brms::VarCorr() |> 
  as.data.frame()
```

## Export Model Results to db

```{r Export Model Results to db, include = T, message = F, warning = F, eval = T, echo = T}
golf::export_lm_round_predictions(
  model = gross_lmer,
  scores_sum = scores_sum
)
```

## Predict Next Round

Predict the next round's `Gross Score` according to the model

```{r Predict the next score using Updated Data, include = T, warning = F, message = F, echo = F}
con <- golf::get_db_connection(db_path = db_path)

round_date <- lubridate::as_date('2026-04-19')
index <- 11.0
course <- "Randolph North"
tees <- 'blue'

new_df <- DBI::dbGetQuery(
  conn = con,
  statement = paste0("SELECT DISTINCT course_name, course_rating
                     FROM courses
                     WHERE course_name
                     LIKE '%", paste0(course), "%'
                     AND tees = '", paste0(tees), "';")
) |> 
  dplyr::as_data_frame() |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    
    index_mean = scores_sum |> 
      dplyr::ungroup() |> 
      dplyr::mutate(
        `Handicap Index` = mean(`Handicap Index`),
        course_name = gsub(date_course,
                           pattern = '[0-9]|\\-|\\\n|\\.',
                           replacement =  '')) |> 
      dplyr::distinct(`Handicap Index`) |> 
      unlist() |> as.numeric(),
    
    `Handicap Index` = index, # enter current index
    
    course_rating_mean = scores_sum |> 
      dplyr::ungroup() |> 
      dplyr::mutate(
        course_rating = mean(course_rating),
        course_name = gsub(date_course,
                           pattern = '[0-9]|\\-|\\\n|\\.',
                           replacement =  '')) |> 
      dplyr::distinct(course_rating) |> 
      unlist() |> as.numeric(),
    
    days = scores_sum |> ## extract the total days since the first score was posted
      dplyr::ungroup() |> 
      dplyr::add_row(date = round_date) |> 
      dplyr::mutate(days = as.numeric(date - min(date) + 1, units = 'days')) |> 
      dplyr::slice_tail() |> 
      dplyr::select(days) |> unlist() |> as.numeric()) |> 
  dplyr::mutate(course_rating = ((course_rating + course_rating_mean)/2) - course_rating,
                `Handicap Index` = ((`Handicap Index` + index_mean)/2) - `Handicap Index`) |> 
  dplyr::select(-course_rating_mean, -index_mean) |> 
  dplyr::rename(course = course_name)
```

```{r Show predictions, include = T, warning = F, message = F, echo = T}
## show the model-predicted gross score for the upcoming round, rounded to the nearest stroke
stats::predict(object = gross_lmer, newdata = new_df, allow.new.levels = T) |>
  as.numeric() %>%
  round(., 0)
```

```{r, results='asis', echo=FALSE}
fmt <- knitr::pandoc_to()

if (identical(fmt, "html")) {
  cat('# Plot Model {.tabset .tabset-pills .tabset-fade}\n')
} else if (identical(fmt, "markdown")) {
  cat('<details><summary><strong>Plot Model</strong></summary>\n')
} else {
  cat('# Plot Model\n')
}
```

## Model Predictions

These predictions are **not** historical-- they are current:

  + i.e. the model did *not* predict anything close to the **72** in August 2025

```{r PlotModels, include = T, message = F, warning = F, echo = F, render = T}
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(course_name = gsub(date_course,
                                   pattern = '[0-9]|\\-|\\\n|\\.',
                                   replacement =  ''), # extract course name
                days = as.numeric(date - min(date), units = 'days') + 1, # include days
                `Predicted Gross` = stats::predict(gross_lmer, re.form = NULL)) |> # add the lmer's predicted Gross Scores
  dplyr::distinct(course_name, course_rating, date, days, `Gross Score`, `Handicap Index`,`Predicted Gross`) |> 
  
  dplyr::add_row(course_name = paste0('Next Round at ', new_df$course)) |> # add projection values
  dplyr::mutate(course_rating = dplyr::case_when(grepl(course_name,pattern = 'Next') ~ DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT course_name, course_rating
                                                                    FROM courses
                                                                    WHERE course_name
                                                                    LIKE '%", paste0(course), "%'
                                                                    AND tees = '",paste0(tees),"';")) |> dplyr::select(course_rating) |> unlist() |> as.numeric(),
                                                 TRUE ~ course_rating),
                date = dplyr::case_when(grepl(course_name, pattern = 'Next') ~ lubridate::as_date(round_date), TRUE ~ date),
                days = dplyr::case_when(grepl(course_name, pattern = 'Next') ~ as.numeric(date - min(date), units = 'days'), TRUE ~ days),
                `Handicap Index` = dplyr::case_when(grepl(course_name, pattern = 'Next') ~ index, TRUE ~ `Handicap Index`),
                `Predicted Gross` = dplyr::case_when(grepl(course_name, pattern = 'Next') ~ stats::predict(object = gross_lmer,
                                                                                                           newdata = new_df,
                                                                                                           allow.new.levels = T) |>
                                                       as.numeric() %>%
                                                       round(., 0), TRUE ~ `Predicted Gross`),
                `Gross Score` = dplyr::case_when(grepl(course_name, pattern = 'Next') ~ `Predicted Gross`, TRUE ~ `Gross Score`)) |> 
  
  dplyr::group_by(course_name) |> 
  ggplot2::ggplot(aes(x = date, y = `Gross Score`, group = course_name, color = course_name, fill = course_name)) +
  ggplot2::geom_point(size = 5, alpha = 0.7, inherit.aes = T) +
  ggplot2::geom_line(aes(x = date, y = `Gross Score`), color = 'black', alpha = 0.5, size = 1.5, inherit.aes = F) +
  ggplot2::geom_line(aes(x = date, y = `Predicted Gross`), color = 'navy', alpha = 0.7, size = 3, inherit.aes = F) +
  ggplot2::geom_smooth(aes(x = date, y = `Gross Score`, group = course_name, color = course_name, fill = course_name), size = 2, method = 'lm', se = F) +
  ggplot2::labs(title = paste0('LMER-Predicted Gross Scores\n(navy or with text)\nas of ', Sys.Date()),
                color = 'Course') +
  ggplot2::theme_bw() +
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 13),
                 panel.grid.minor = ggplot2::element_blank(),
                 legend.title = ggplot2::element_text(face = 'bold', size = 11),
                 legend.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.key.width = rel(0.4),
                 legend.key.height = rel(0.4),
                 legend.key.spacing.y = rel(0.4),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text.x = ggplot2::element_text(face = 'bold', size = 9, angle = 270, hjust = 0, vjust = 0.5),
                 axis.text.y = ggplot2::element_text(face = 'bold', size = 9)
                 ) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b') +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_text(aes(x = lubridate::as_date(round_date),
                         y = stats::predict(object = gross_lmer,
                                                newdata = new_df,
                                                allow.new.levels = T) |>
                           as.numeric() %>%
                           round(., 0),
                         label = stats::predict(object = gross_lmer,
                                                newdata = new_df,
                                                allow.new.levels = T) |>
                           as.numeric() %>%
                           round(., 0)),
                     inherit.aes = F, size = 3, color = 'black', hjust = -0.1)
```

The model is a random intercept, random slope model.

In this case, that means `Gross Score` varies in its deviation from the overall mean `Gross Score` over time: `Silverbell`, `Randolph North`, and `Dell Urich` have their own slopes at different intercepts/heights along the y-axis.

+ The `gray` line just connects each sequential round (`Gross Score`) over time
+ The `blue` line is the model's predictions of each `Gross Score`, accounting for `course`, `course_rating`, `Handicap Index`, and `days` (time)
+ `Silverbell`'s line represents the relationship between `Gross Score`, `course_rating`, `Handicap Index`, and `days` (date/time) at `Silverbell`
+ `Randolph`'s line represents the relationship between `Gross Score`, `course_rating`, `Handicap Index`, and `days` (date/time) at `Randolph North`
+ `Dell Urich`'s line represents the relationship between `Gross Score`, `course_rating`, `Handicap Index`, and `days` (date/time) at `Dell Urich`

## Actual Gross Score vs Predicted Gross Score

```{r PlotActualVsPredictedGross, include = T, message = F, warning = F, echo = F, render = T}
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1, # include days
    
    `Predicted Gross` = stats::predict(
      gross_lmer,
      re.form = NULL)) |> # add the lmer's predicted Gross Scores
  
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Predicted Gross`,
                  `Net Score`) |> 
  
  dplyr::mutate(residual = `Gross Score` - `Predicted Gross`) |> 
  ggplot2::ggplot(aes(x = date,
                      y = residual,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Performance vs Prediction\nfrom ',
                               scores |> 
                                 dplyr::ungroup() |> 
                                 dplyr::arrange(date) |>  
                                 dplyr::select(date) |> 
                                 unlist() |> lubridate::as_date() |> 
                                 dplyr::first() |> as.character(),
                               ' - present\nas of ',
                               Sys.Date()),
                               
                x = 'date',
                y = 'Actual Gross Score - Predicted Gross Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8),
                 legend.key.height = rel(0.4),
                 legend.key.width = rel(0.4),
                 legend.key.spacing.y = rel(0.4)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = date, y = residual), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = date, y = residual), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = date, y = residual, label = `Handicap Index`),
                     size = 3, color = 'black')
```

## Actual Net Score vs Predicted Gross Score

```{r PlotActualNetVsPredictedGross, include = T, message = F, warning = F, echo = F, render = T}
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1, # include days
    
    `Predicted Gross` = stats::predict(
      gross_lmer,
      re.form = NULL)) |> # add the lmer's predicted Gross Scores
  
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Predicted Gross`,
                  `Net Score`) |> 
  
  dplyr::mutate(residual = `Predicted Gross` - `Net Score`) |> 
  ggplot2::ggplot(aes(x = date,
                      y = residual,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Performance vs Prediction\nfrom ',
                               scores |> 
                                 dplyr::ungroup() |> 
                                 dplyr::arrange(date) |>  
                                 dplyr::select(date) |> 
                                 unlist() |> lubridate::as_date() |> 
                                 dplyr::first() |> as.character(),
                               ' - present\nas of ',
                               Sys.Date()),
                x = 'date',
                y = 'Predicted Gross Score - Net Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = date, y = residual), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = date, y = residual), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = date, y = residual, label = `Handicap Index`),
                     size = 3, color = 'black')
```

## Actual Gross Score vs Course Rating

```{r PlotGrossScoreVsCourseRating, include = T, warning = F, message = F, echo = F, render = T}
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1) |>  # include days
  
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Net Score`) |> 
  ggplot2::ggplot(aes(y = `Gross Score`,
                      x = course_rating,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Gross Score vs Course Difficulty\nfrom ',
                               scores |>
                                 dplyr::ungroup() |>
                                 dplyr::arrange(date) |>
                                 dplyr::select(date) |>
                                 unlist() |> lubridate::as_date() |>
                                 dplyr::first() |> as.character(),
                               ' - present\nas of ',
                               Sys.Date()),
                x = 'Course Rating',
                y = 'Gross Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = course_rating, y = `Gross Score`), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = course_rating, y = `Gross Score`), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = course_rating, y = `Gross Score`,
                         label = `Handicap Index`),
                     size = 3, color = 'black')
```

## Actual Gross Score vs Handicap Index

```{r PlotGrossScoreVsHandicapIndex, include = T, message = F, warning = F, echo = F, render = T}
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1) |> # include days
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Net Score`) |>  
  ggplot2::ggplot(aes(x = `Handicap Index`,
                      y = `Gross Score`,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Gross Score vs Handicap Index\nfrom ',
                               scores |>
                                 dplyr::ungroup() |>
                                 dplyr::arrange(date) |>
                                 dplyr::select(date) |>
                                 unlist() |> lubridate::as_date() |>
                                 dplyr::first() |> as.character(),
                               ' - present\nas of ',
                               Sys.Date()),
                x = 'Handicap Index',
                y = 'Gross Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = `Handicap Index`, y = `Gross Score`), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = `Handicap Index`, y = `Gross Score`), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = `Handicap Index`, y = `Gross Score`, label = `Handicap Index`),
                     size = 3, color = 'black')
```


```{r PlotGrossScoreVsHandicapIndexWithout72, include = F, message = F, warning = F, echo = F, render = F}
## Actual Gross Score vs Handicap Index, 72 removed
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1) |> # include days
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Net Score`) |>  
  dplyr::filter(!grepl(date, pattern = '2025-08-03')) |> 
  ggplot2::ggplot(aes(x = `Handicap Index`,
                      y = `Gross Score`,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Gross Score vs Handicap Index\nfrom ',
                               scores |>
                                 dplyr::ungroup() |>
                                 dplyr::arrange(date) |>
                                 dplyr::select(date) |>
                                 unlist() |> lubridate::as_date() |>
                                 dplyr::first() |> as.character(),
                               ' - present\n(removing outlier 72)\nas of ',
                               Sys.Date()),
                x = 'Handicap Index',
                y = 'Gross Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = `Handicap Index`, y = `Gross Score`), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = `Handicap Index`, y = `Gross Score`), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = `Handicap Index`, y = `Gross Score`, label = `Handicap Index`),
                     size = 3, color = 'black')
```


## Actual Net Score vs Course Rating

```{r PlotNetScoreVsCourseDifficulty, include = T, warning = F, message=F, echo = F, render = T}
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1
    ) |> # add the lmer's predicted Gross Scores
  
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Net Score`) |> 
  ggplot2::ggplot(aes(y = `Net Score`,
                      x = course_rating,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Net Score vs Course Difficulty\nfrom ',
                               scores |>
                                 dplyr::ungroup() |>
                                 dplyr::arrange(date) |>
                                 dplyr::select(date) |>
                                 unlist() |> lubridate::as_date() |>
                                 dplyr::first() |> as.character(),
                               ' - present\nas of ',
                               Sys.Date()),
                x = 'Course Rating',
                y = 'Net Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = course_rating, y = `Net Score`), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = course_rating, y = `Net Score`), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = course_rating, y = `Net Score`, label = `Handicap Index`),
                     size = 3, color = 'black')
```

```{r PlotNetScoreVsCourseRatingWithout72AndCombos, include = F, message = F, warning= F, echo = F, render = F}

## Actual Net Score vs Course Rating without 72 and Combo Tees
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1 # include days
    ) |> # add the lmer's predicted Gross Scores
  dplyr::filter(!(grepl(course_name, pattern = 'Dell') &
                   course_rating != 67.8) &
                  !(grepl(course_name, pattern = 'Rand') &
                      course_rating != 69.8)) |> 
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Net Score`) |> 
  dplyr::filter(!grepl(date, pattern = '2025-08-03')) |> 
  ggplot2::ggplot(aes(y = `Net Score`,
                      x = course_rating,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Net Score vs Course Difficulty\nfrom ',
                               scores |>
                                 dplyr::ungroup() |>
                                 dplyr::arrange(date) |>
                                 dplyr::select(date) |>
                                 unlist() |> lubridate::as_date() |>
                                 dplyr::first() |> as.character(),
                               ' - present\n(removing outlier 72 and long combo rounds)\nas of ',
                               Sys.Date()),
                x = 'Course Rating',
                y = 'Net Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = course_rating, y = `Net Score`), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = course_rating, y = `Net Score`), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = course_rating, y = `Net Score`, label = `Handicap Index`),
                     size = 3, color = 'black')
```