---
title: "LMER Model Predictions"
author: "Erik Larsen"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    fig_width: 10
    fig_height: 10
    code_folding: hide
  pdf_document:
    fig_width: 10
    fig_height: 10
    latex_engine: xelatex
  md_document:
    variant: gfm
---

### Overview

This markdown is:

+ a rough proxy for a tutorial on interpreting linear mixed model outputs

+ a light introduction to golf scoring systems 

The markdown shows: 

+ the linear mixed model used to measure my performance for each golf round and predict my performance in the next golf round

The model does this by incorporating my skill level and where I've played in the past

### Introduction {.tabset .tabset-pills .tabset-fade}

Skill level is officially determined by the **USGA** as a `Handicap Index`: how many strokes, on average, a player takes to complete a round at a given course with a given difficulty relative to that course's average:

  + a player with a **10.0** `Handicap Index` is expected, on average, to take **82 strokes** to complete a round at a course where the average number of strokes has been determined to be **72**
  
`Gross Score` is a total number of strokes taken by a given player for any individual hole

  + this is extrapolated across each of 18 holes, so while `Gross Score` can mean a total of strokes for a hole *or* a total of strokes for a round, in this markdown, **it is per round**
  
  + the average `Gross Score` over a player's best **8 rounds** *from their last 20* is used to determine their `Handicap Index`
  
Thus, this markdown shows the model used to predict the opposite:

  + given my `Handicap Index` and `Gross Score`s at previous courses of varying difficulty in the past,
  
    + **what will be my next** `Gross Score`?
    
Note that I use the terms, `strokes`, and, `shots`, interchangeably, though putts are not connoted as `shots`

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 10,
  dev = c("png", "pdf"),
  fig.path = "../figures/LMER_predictions/"
)

real_db <- fs::path_abs("inst/extdata/golf.duckdb")
# real_db <- fs::path_abs(paste0(getwd(), "../../inst/extdata/golf.duckdb"))
con <- golf::get_db_connection(db_path = real_db)

golf::refresh_dev_tables()
```

### Gather Data and Format Scores {.tabset .tabset-pills .tabset-fade}

#### Attach Packages

```{r Attach Packages, include = T, message = F, warning = F, echo = T}
library(golf)
library(tidyverse)
library(lme4)
library(DBI)
```

#### Gather Scores

Gather and format from the database

```{r Summarize Metrics out, include = T, message = F, warning = F, echo = T, eval = F}
## connect to the db
con <- golf::get_db_connection()

scores <- DBI::dbGetQuery(conn = con, statement = paste0(
  "SELECT DISTINCT r.*, c.par, c.course_rating, c.slope FROM rounds r
  INNER JOIN courses c
  ON c.tees = r.tees
  AND c.course_name = r.course_name
  AND c.hole = r.hole
  INNER JOIN players p
  ON r.GHIN = p.GHIN
  AND r.handicap_index = p.handicap_index
  AND r.date = p.date;"
)) |> 
  dplyr::mutate(date = lubridate::as_date(date), # convert strings to date's
                hole = gsub(hole, pattern = 'hole_', replacement = '') |> # enforce hole order
                  as.numeric()) |> 
  dplyr::relocate(par, .after = hole) |> 
  dplyr::relocate(course_rating, .after = tees) |>
  dplyr::group_by(date) |> 
  dplyr::arrange(desc(date), hole) |> 
  dplyr::ungroup()
```

```{r Summarize Metrics in, include = T, message = F, warning = F, echo = F, eval = T}
## connect to the db
con <- golf::get_db_connection()

scores <- DBI::dbGetQuery(conn = con, statement = paste0(
  "SELECT DISTINCT r.*, c.par, c.course_rating, c.slope FROM dev_rounds r
  INNER JOIN courses c
  ON c.tees = r.tees
  AND c.course_name = r.course_name
  AND c.hole = r.hole
  INNER JOIN players p
  ON r.GHIN = p.GHIN
  AND r.handicap_index = p.handicap_index
  AND r.date = p.date;"
)) |> 
  dplyr::mutate(date = lubridate::as_date(date), # convert strings to date's
                hole = gsub(hole, pattern = 'hole_', replacement = '') |> # enforce hole order
                  as.numeric()) |> 
  dplyr::relocate(par, .after = hole) |> 
  dplyr::relocate(course_rating, .after = tees) |>
  dplyr::group_by(date) |> 
  dplyr::arrange(desc(date), hole) |> 
  dplyr::ungroup()
```


#### Compute Metrics

Compute standard metrics

```{r Compute Standard Metrics 1, include = T, warning = F, message = F, echo = F}
scores_sum <- scores |>
  dplyr::mutate(date_course = paste0(date,
                                     '\n',
                                     course_name, '\n',
                                     handicap_index),
                chips = dplyr::case_when(
                  grepl(date, pattern = '07-13') ~ NA_real_, TRUE ~ chips),
                `chips+putts` = chips+putts,
                FIR_opps = dplyr::case_when(par > 3 ~ 1, TRUE ~ NA),
                `Iron FIRs` = dplyr::case_when(par > 3 &
                                                 grepl(tee_club, pattern = '4|5') &
                                                 FIR == 1 ~ 1,
                                               TRUE ~ 0),
                `Iron FIR opps` = dplyr::case_when(par > 3 &
                                                     grepl(tee_club, pattern = '4|5') ~ 1,
                                                   TRUE ~ 0),
                `Driver FIRs` = dplyr::case_when(par > 3 &
                                                   tee_club == 'D' &
                                                   FIR == 1 ~ 1,
                                                 TRUE ~ 0),
                `Driver FIR opps` = dplyr::case_when(par > 3 &
                                                     tee_club == 'D' ~ 1,
                                                   TRUE ~ 0),
                `Par 3 GIRs` = dplyr::case_when(par == 3 & 
                                                  GIR == 1 ~ 1,
                                                TRUE ~ 0),
                greenie_putts = dplyr::case_when(GIR == 1 ~ putts, TRUE ~ NA_real_),
                updown_conv = dplyr::case_when(GIR == 0 &
                                                 par == gross ~ 1,
                                               TRUE ~ 0),
                updown_opps = dplyr::case_when(GIR == 0 &
                                                chips > 0 ~ 1,
                                              TRUE ~ 0)
                ) |> 
  dplyr::rename(`Handicap Index` = handicap_index) |> 
  dplyr::group_by(GHIN, date, date_course, course_rating, `Handicap Index`) |> 
  dplyr::summarize(
                   FIRs = sum(FIR, na.rm = F),
                   `Iron FIRs` = sum(`Iron FIRs`, na.rm = T),
                   `Iron FIR%` = round(((sum(`Iron FIRs`, na.rm = T)/sum(`Iron FIR opps`, na.rm = T))*100), 1),
                   `Driver FIRs` = sum(`Driver FIRs`, na.rm = T),
                   `Driver FIR%` = round(((sum(`Driver FIRs`, na.rm = T)/sum(`Driver FIR opps`, na.rm = T))*100), 1),
                   `FIR%` = round((sum(FIRs, na.rm = T)/sum(FIR_opps, na.rm = T))*100, 1),
                   GIRs = sum(GIR, na.rm = F),
                   `Par 3 GIRs` = sum(`Par 3 GIRs`, na.rm = T),
                   `GIR%` = round((sum(GIRs, na.rm = T)/18)*100, 1),
                   putts = sum(putts, na.rm = F),
                   `Avg GIR putts` = round(mean(greenie_putts, na.rm = T), 2),
                   chips = sum(chips, na.rm = F),
                   `chips+putts` = sum(`chips+putts`, na.rm = F),
                   `UpDown%` = round(((sum(updown_conv, na.rm = T)/sum(updown_opps, na.rm = T))*100), 1),
                   pars = sum(is_gross_par, na.rm = F),
                   birdies = sum(is_gross_birdie, na.rm = F),
                   bogies = sum(is_gross_bogey, na.rm = F),
                   `doubles+` = sum(is_gross_bogey_worse, na.rm = F),
                   penalties = sum(penalties, na.rm = T),
                   `Gross Score` = mean(tot_gross, na.rm = F),
                   `Net Score` = mean(tot_net, na.rm = F)) %>%
  dplyr::mutate(dplyr::across(c(`Iron FIRs`, `Driver FIRs`, `Iron FIR%`, `Driver FIR%`, `FIR%`), ~dplyr::if_else(is.na(FIRs), NA, .)),
                dplyr::across(c(`Par 3 GIRs`, `Avg GIR putts`, `UpDown%`, `GIR%`), ~dplyr::if_else(is.na(GIRs), NA, .)),
                `chips+putts` = dplyr::case_when(is.na(chips) ~ NA_real_,
                                                 TRUE ~ `chips+putts`)) %>% 
  dplyr::mutate(`UpDown%` = dplyr::case_when(grepl(date, pattern = '07-13|09-21') ~ NA, TRUE ~ `UpDown%`),
                `Iron FIR%` = dplyr::case_when(`Iron FIR%` == NaN ~ 0.0, TRUE ~ `Iron FIR%`))
```


#### Scoring Metrics

Show Per-Round `Gross Score`s, `Net Score`s and `Handicap Index`

```{r Separate By Type 1, include = T, warning = F, message = F, echo = T}
scoring_metrics <- scores_sum |> 
  dplyr::select(`Handicap Index`, `Gross Score`, `Net Score`)
head(scoring_metrics |> 
       dplyr::arrange(desc(date)))
```

#### Stroke Metrics

In golf, every hole has a `par`-- an average number of strokes taken to get the 
ball in the hole

There are (almost always), three different `par`s on every course: 

+ `par 3`s
+ `par 4`s
+ `par 5`s

A shorthand to determine how a golfer performed across holes is to rate how many 
strokes *relative to par* they were (-1, -2, +1, +2, etc)

These numbers are given names:

+ `0 = par`
+ `-2 = eagle`
+ `-1 = birdie`
+ `+1 = bogey`
+ `+2 = double bogey`

I quantify these below:

```{r Separate By Type 2, include = T, warning = F, message = F, echo = T}
stroke_metrics <- scores_sum |> 
  dplyr::select(`doubles+`, bogies, pars, birdies)
head(stroke_metrics |> 
       dplyr::arrange(desc(date)))
```

#### Around-the-Green Metrics

`Chips`: 
  + strokes around the green taken to get onto the green

`Putts`:
  + strokes taken with the putter on the green
  
`Avg GIR putts`:
  + Average # of putts on holes where the ball was hit on to the green within 2 strokes of par (green in regulation, `GIR`)
  
`UpDown%` (aka `Scramble%`):
  + # of holes without a `GIR` but par was made / 
  # of holes without a `GIR`

```{r Separate By Type 3, include = T, warning = F, message = F, echo = T}
atg_metrics <- scores_sum |> 
  dplyr::select(chips, `chips+putts`, `UpDown%`, putts, `Avg GIR putts`)
head(atg_metrics |> 
       dplyr::arrange(desc(date)))
```

#### Ball Striking

Approach and tee accuracy

`GIR (green in regulation)`:
  + hole where the ball was hit on to the green within 2 strokes of par
  
`FIR (fairway in regulation)`:
  + hole where the ball was hit on to the fairway from the tee box (only on par 4's and par 5's)
  
`Iron FIR`:
  + hole where an iron was used off the tee for a `FIR`
  
`Driver FIR`:
  + hole where driver was used off the tee for a `FIR`

```{r Separate By Type 4, include = T, warning = F, message = F, echo = T}
ball_striking_metrics <- scores_sum |> 
  dplyr::select(GIRs, `GIR%`, `Par 3 GIRs`,
                FIRs, `FIR%`, `Iron FIRs`, `Iron FIR%`,
                `Driver FIRs`, `Driver FIR%`)
head(ball_striking_metrics |> 
       dplyr::arrange(desc(date)))
```

#### Shot Quality

Yardage and accuracy on tracked shots

```{r Stroke Quality out, include = T, warning= F, message = F, echo = T, eval = F}
## connect to the db
con <- golf::get_db_connection()

stroke_quality <- DBI::dbGetQuery(conn = con,
                                  statement = paste0("SELECT DISTINCT * FROM club_metrics;")) |>
  dplyr::mutate(date = lubridate::as_date(date),
                hole = gsub(hole, pattern = 'hole_', replacement = ''),
                hole = as.integer(hole)) |> 
  dplyr::mutate(dplyr::across(dplyr::contains("yds"), ~as.integer(.x))) |> 
  dplyr::rename(course = course_name) |> 
  dplyr::group_by(date, hole, stroke) |> 
  dplyr::arrange(date, hole, stroke)
head(stroke_quality |> 
       dplyr::arrange(desc(date)))
```

```{r Stroke Quality in, include = T, warning = F, message = F, echo = F, eval = T}
## connect to the db
con <- golf::get_db_connection()

stroke_quality <- DBI::dbGetQuery(conn = con,
                                  statement = paste0("SELECT DISTINCT * FROM dev_club_metrics;")) |>
  dplyr::mutate(date = lubridate::as_date(date),
                hole = gsub(hole, pattern = 'hole_', replacement = ''),
                hole = as.integer(hole)) |> 
  dplyr::mutate(dplyr::across(dplyr::contains("yds"), ~as.integer(.x))) |> 
  dplyr::rename(course = course_name) |> 
  dplyr::group_by(date, hole, stroke) |> 
  dplyr::arrange(date, hole, stroke)
head(stroke_quality |> 
       dplyr::arrange(desc(date)))
```


```{r Stroke Quality Metrics, include = F, warning = F, message = F, echo = F}
stroke_quality_min <- stroke_quality |> 
  dplyr::group_by(club) |> 
  dplyr::summarize()
```

### Fit a LMER Model {.tabset .tabset-pills .tabset-fade}

Fit a lmer model to capture repeated measurements of `Gross Score` 
predicted by `Handicap Index`, `course_rating`, and time (`days`).

+ Every course has a rating; the `Handicap Index` calculation factors in these ratings

+ Center the `course_rating` and `Handicap Index` variables at their mean to make interpreting intercept and slope estimates more meaningful

+ Include random intercepts and random slopes of `course` and `course_rating`, given
a `Handicap Index`

```{r Fit the model, include = T, message = F, warning = F, echo = T}
# Fit a model to the data

gross_lmer <- lme4::lmer(
  
  data = scores_sum |> 
    dplyr::ungroup() |> 
    dplyr::mutate(
      
      course_rating = course_rating - mean(course_rating),
      
      course = gsub(date_course,
                    pattern = '[0-9]|\\-|\\\n|\\.',
                    replacement = ''), # extract the course names
      
      `Handicap Index` = -`Handicap Index` - mean(-`Handicap Index`),
      days = as.numeric(as.Date(date) - min(as.Date(date)) + 1,
                        units = 'days')
      ) |> # create a 'days' metric starting at the first day joining the club 
    
    dplyr::relocate(days, .after = date),
  
  formula = 
    `Gross Score` ~
    `Handicap Index`*course_rating +
    days +
    (1 + `Handicap Index`|course) #+ # random intercepts and random slopes for Gross Score at a given course, given a certain index
    # (1 + `Handicap Index`|course_rating) # random intercepts and random slopes for Gross Score at a given course difficulty, given a certain index
           ) # somewhat redundant
```

#### LMER Model Summary

```{r Show Model results, include = T, message = F, warning = F, eval = T, echo = F}
summary(gross_lmer)
```
```{r Extract RE, include = T, message = F, warning = F, eval = T, echo = F}
vc_df <- gross_lmer |> 
  brms::VarCorr() |> 
  as.data.frame()
```

### Model Interpretations {.tabset .tabset-pills .tabset-fade}

#### Fixed Effects {.tabset .tabset-pills .tabset-fade}

##### Gross Score Intercept

The model's estimated average *first* `Gross Score` (**`(Intercept)` `Estimate` of `Fixed effects`**) at my average `Handicap Index` and average `course_rating` at `Arizona National` (default reference course) is **`r nlme::fixed.effects(gross_lmer)['(Intercept)'] |> as.numeric() %>% round(.,2)`**.

My average `Gross Score`, however, is **`r scores_sum |> dplyr::ungroup() |> dplyr::rename(Gross_Score = 25) |> dplyr::summarize(avg_gross = mean(Gross_Score)) |> unlist() |> as.numeric() %>% round(.,2)`**. 

##### Handicap Index

For every additional `Handicap Index` point improvement (lower) than my average `Handicap Index`, my expected `Gross Score` decreases by **`r nlme::fixed.effects(gross_lmer) |> as.data.frame() |> tibble::rownames_to_column('coef') |> dplyr::filter(grepl(coef, pattern = 'Index.$')) |> dplyr::select(2) |> unlist() |> as.numeric() %>% round(., 2) |> abs()`** strokes.

+ This makes sense because `Gross Score` is used to directly determine `Handicap Index` and is positively correlated:

  + high `Gross Score` = high `Handicap Index`

  + In other words, a player with better skill will have a lower `Handicap Index`
  
    + An example: a player with a **0** index means they average `par` (the course average) for an entire round, across rounds, while a worse player (who averages above `par`, the course average) will have a higher `Handicap Index`
  
    + `Handicap Index` corrects for skill-level

  + The effect is `r if (stats::coef(summary(gross_lmer)) |> as.data.frame() |> tibble::rownames_to_column('coef') |> dplyr::filter(grepl(coef, pattern = 'Index.$')) |> dplyr::select(4) |> as.numeric() |> abs() > 1) { paste0('significant') } else { paste0('not significant') }` 
  (**`t value` = `r stats::coef(summary(gross_lmer)) |> as.data.frame() |> tibble::rownames_to_column('coef') |> dplyr::filter(grepl(coef, pattern = 'Index.$')) |> dplyr::select(dplyr::contains("value")) |> unlist() |> as.numeric() %>% round(., 2)`**; significance : abs(**t value**) > 1)
  
  + Again, `Handicap Index` is a metric *directly derived from* `Gross Score`
  
    + I'm unsure how many strokes (`Gross Score`) index points *should* be worth! **1?** **More?**
    
    + Does it vary by skill, or is it uniform?
    
##### Course Rating

For every additional `course_rating` point (aka, a stroke) greater than the average `course_rating` (~69-70 strokes in this dataset), `Gross Score` increases by **`r nlme::fixed.effects(gross_lmer)[3] |> as.numeric() %>% round(.,2)`** strokes (it decreases).

  + This also makes sense: harder courses should yield higher `Gross Score`s
  
##### Time (days)

For every additional `day` in time, my `Gross Score` drops by **`r nlme::fixed.effects(gross_lmer)['days'] |> as.numeric() %>% round(.,2)`** strokes

  + While this seems tiny, extrapolating days to months or weeks, this becomes very evident (**`r nlme::fixed.effects(gross_lmer)['days'] |> as.numeric() %>% round(.,2)*30`** strokes per month; **`r nlme::fixed.effects(gross_lmer)['days'] |> as.numeric() %>% round(.,2)*365`** strokes per year)

  + Linear extrapolation in this sense is misleading: there will be a limit to lowering `Gross Score` and there will also be variation in the process

  + But this effect is strongly significant (**t value = ** **`r stats::coef(summary(gross_lmer))['days', 't value'] |> as.numeric() %>% round(., 2)`**) and appears to be the primary driver of the trend
  
##### Handicap Index*Course Rating Interaction

As `course_rating` increases by 1 stroke above average, the effect of `Handicap Index` on my expected `Gross Score` is **`r nlme::fixed.effects(gross_lmer) |> as.data.frame() |> tibble::rownames_to_column('coef') |> dplyr::slice_tail() |>  dplyr::select(2) |> unlist() |> as.numeric() %>% abs() %>% round(.,2)`** strokes less than what the two effects would contribute independently.

  + In other words: hard courses already impose a big penalty, so the *extra* penalty by playing worse than average is smaller
  + Related: easier courses impose a larger *extra* penalty by playing worse than average
  + Related: harder courses add a larger bonus when playing better than average
  + Related: easier courses add a smaller bonus when playing better than average

#### Random Effects {.tabset .tabset-pills .tabset-fade}

##### Course, Handicap Index, and Time

These `courses` vary in their difficulty, independent of player skill (`Handicap Index`), by ~ **+/- `r vc_df |> dplyr::filter(grp == 'course' & grepl(var1, pattern = 'Int') & is.na(var2)) |> dplyr::select(sdcor) |>  as.numeric() %>% round(., 2)`** strokes. This value is the **`Random effects` `Std. Dev.` (`Intercept`) from the model summary**-- the `Std.Dev.` of the course-level random intercepts, representing how much each course shifts my baseline expected `Gross Score` up or down relative to the overall average, *even after accounting for `course_rating`*.

  + I play different courses much differently

Interestingly, `courses` also differ slightly in how sensitive they are to my `Handicap Index`, with a random-slope standard deviation of **+/- `r vc_df |> dplyr::filter(grp == 'course' & grepl(var1, pattern = 'Handicap') & is.na(var2)) |> dplyr::select(sdcor) |>  as.numeric() %>% round(., 2)`** strokes per index point.

While there is a fair amount of variability in `Gross Score` driven by the `course`, there is also just a large amount of variability in `Gross Score`, overall: **`r vc_df |> dplyr::filter(grp == 'Residual') |> dplyr::select(sdcor) |> unlist() |> as.numeric() %>% round(., 2)`**. This is the `Random effects` `Residual` `Std.Dev.` from the model summary.

### Predict the Next Round {.tabset .tabset-pills .tabset-fade}

Predict the next round's `Gross Score` according to the model

```{r Predict the next score using Updated Data, include = T, warning = F, message = F, echo = F}
con <- golf::get_db_connection()

round_date <- lubridate::as_date('2026-08-16')
index <- 9.8
course <- "Dell Urich"
tees <- 'combo'

## get updated data to predict the next round
new_df <- DBI::dbGetQuery(
  conn = con,
  statement = paste0("SELECT DISTINCT course_name, course_rating
                     FROM courses
                     WHERE course_name
                     LIKE '%", paste0(course), "%'
                     AND tees = '", paste0(tees), "';")
) |> 
  dplyr::as_data_frame() |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    
    index_mean = scores_sum |> 
      dplyr::ungroup() |> 
      dplyr::mutate(
        `Handicap Index` = mean(`Handicap Index`),
        course_name = gsub(date_course,
                           pattern = '[0-9]|\\-|\\\n|\\.',
                           replacement =  '')) |> 
      dplyr::distinct(`Handicap Index`) |> 
      unlist() |> as.numeric(),
    
    `Handicap Index` = index, # enter current index
    
    course_rating_mean = scores_sum |> 
      dplyr::ungroup() |> 
      dplyr::mutate(
        course_rating = mean(course_rating),
        course_name = gsub(date_course,
                           pattern = '[0-9]|\\-|\\\n|\\.',
                           replacement =  '')) |> 
      dplyr::distinct(course_rating) |> 
      unlist() |> as.numeric(),
    
    days = scores_sum |> ## extract the total days since the first score was posted
      dplyr::ungroup() |> 
      dplyr::add_row(date = round_date) |> 
      dplyr::mutate(days = as.numeric(date - min(date) + 1, units = 'days')) |> 
      dplyr::slice_tail() |> 
      dplyr::select(days) |> unlist() |> as.numeric()) |> 
  dplyr::mutate(course_rating = course_rating - ((course_rating + course_rating_mean)/2),
                `Handicap Index` = `Handicap Index` - ((`Handicap Index` + index_mean)/2)) |> 
  dplyr::select(-course_rating_mean, -index_mean) |> 
  dplyr::rename(course = course_name)
```

##### Show Prediction

```{r Show predictions, include = T, warning = F, message = F, echo = T}
## show the model-predicted gross score for the upcoming round, rounded to the nearest stroke
stats::predict(object = gross_lmer, newdata = new_df, allow.new.levels = T) |>
  as.numeric() %>%
  round(., 0)
```

#### Plot the Model {.tabset .tabset-pills .tabset-fade}

##### Model by Course

```{r PlotModelByCourse, include = T, message = F, warning = F, echo = F, render = T}
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(course_name = gsub(date_course,
                                   pattern = '[0-9]|\\-|\\\n|\\.',
                                   replacement =  ''), # extract course name
                days = as.numeric(date - min(date), units = 'days') + 1, # include days
                `Predicted Gross` = stats::predict(gross_lmer, re.form = NULL)) |> # add the lmer's predicted Gross Scores
  dplyr::distinct(course_name, course_rating, date, days, `Gross Score`, `Handicap Index`,`Predicted Gross`) |> 
  
  dplyr::add_row(course_name = 'mean') |> # add all mean values
  dplyr::mutate(course_rating = dplyr::case_when(course_name == 'mean' ~ mean(course_rating, na.rm = T), TRUE ~ course_rating),
                days = dplyr::case_when(course_name == 'mean' ~ mean(days, na.rm = T), TRUE ~ days),
                `Gross Score` = dplyr::case_when(course_name == 'mean' ~ scores_sum |> 
                                                   dplyr::ungroup() |> dplyr::summarize(avg = round(mean(`Gross Score`), 0)) |> unlist() |> as.numeric(), 
                                                 TRUE ~ `Gross Score`),
                date = dplyr::case_when(course_name == 'mean' ~ mean(date, na.rm = T), TRUE ~ date),
                `Handicap Index` = dplyr::case_when(course_name == 'mean' ~ mean(`Handicap Index`, na.rm = T), TRUE ~ `Handicap Index`),
                `Predicted Gross` = dplyr::case_when(course_name == 'mean' ~ mean(`Predicted Gross`, na.rm = T), TRUE ~ `Predicted Gross`)) |>
  
  dplyr::group_by(course_name) |> 
  ggplot2::ggplot(aes(x = date, y = `Gross Score`, group = course_name, color = course_name, fill = course_name)) +
  ggplot2::geom_point(aes(alpha = 0.1),size = 3, inherit.aes = T) +
  ggplot2::geom_line(aes(x = date, y = `Gross Score`), color = 'black', alpha = 0.3, size = 1.5, inherit.aes = F) +
  ggplot2::geom_line(aes(x = date, y = `Predicted Gross`), color = 'navy', alpha = 0.5, size = 3, inherit.aes = F) +
  ggplot2::geom_text(aes(x = date, y = `Gross Score`, label = `Gross Score`, fontface = 'bold'), color = 'black', size = 4) +
  
  ggplot2::geom_smooth(aes(x = date, y = `Gross Score`, group = course_name, color = course_name, fill = course_name), method = 'lm', se = F) +
  ggplot2::labs(title = paste0('Linear Mixed Effects Regression (LMER) Model\ntrained on Gross Scores\nas of ', Sys.Date()),
                color = 'Course') +
  ggplot2::theme_bw() +
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 13),
                 panel.grid.minor = ggplot2::element_blank(),
                 legend.title = ggplot2::element_text(face = 'bold', size = 11),
                 legend.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.key.width = rel(0.4),
                 legend.key.height = rel(0.4),
                 legend.key.spacing.y = rel(0.4),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text.x = ggplot2::element_text(face = 'bold', size = 9, angle = 270, hjust = 0, vjust = 0.5),
                 axis.text.y = ggplot2::element_text(face = 'bold', size = 9),
                 strip.background = ggplot2::element_rect(fill = 'white', color = 'black'),
                 strip.text = ggplot2::element_text(face = 'bold', size = 10)
                 ) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b') +
  ggplot2::guides(fill = 'none', alpha = 'none') +
  ggplot2::facet_wrap(~course_name)
```

The model is a random intercept, random slope linear mixed-effects regression (LMER) model.

In this case, that means `Gross Score` varies for each course at a given `Handicap Index` in its deviation from the overall mean `Gross Score` (navy blue line) over time: `Silverbell`, `Randolph North`, and `Dell Urich` have their own average `Gross Scores` (intercepts) and slopes (change in `Gross Score` over time)-- notice how the line for each course has a different slope, starting at a different y-intercept

+ The `blue` line is the model's overall fit of the `Gross Score`, accounting for `course`, `course_rating`, `Handicap Index`, and `days` (time)
+ `Silverbell`'s line represents the relationship between `Gross Score`, `course_rating`, `Handicap Index`, and `days` (date/time) at `Silverbell`
+ `Randolph`'s line represents the relationship between `Gross Score`, `course_rating`, `Handicap Index`, and `days` (date/time) at `Randolph North`
+ `Dell Urich`'s line represents the relationship between `Gross Score`, `course_rating`, `Handicap Index`, and `days` (date/time) at `Dell Urich`

##### Model Predictions

These predictions are **not** historical-- they are current:

  + i.e. the model did *not* predict anything close to the **72** in August 2025

```{r PlotModels, include = T, message = F, warning = F, echo = F, render = T}
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(course_name = gsub(date_course,
                                   pattern = '[0-9]|\\-|\\\n|\\.',
                                   replacement =  ''), # extract course name
                days = as.numeric(date - min(date), units = 'days') + 1, # include days
                `Predicted Gross` = stats::predict(gross_lmer, re.form = NULL)) |> # add the lmer's predicted Gross Scores
  dplyr::distinct(course_name, course_rating, date, days, `Gross Score`, `Handicap Index`,`Predicted Gross`) |> 
  
  dplyr::add_row(course_name = paste0('Next Round at ', new_df$course)) |> # add projection values
  dplyr::mutate(course_rating = dplyr::case_when(grepl(course_name,pattern = 'Next') ~ DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT course_name, course_rating
                                                                    FROM courses
                                                                    WHERE course_name
                                                                    LIKE '%", paste0(course), "%'
                                                                    AND tees = '",paste0(tees),"';")) |> dplyr::select(course_rating) |> unlist() |> as.numeric(),
                                                 TRUE ~ course_rating),
                date = dplyr::case_when(grepl(course_name, pattern = 'Next') ~ lubridate::as_date(round_date), TRUE ~ date),
                days = dplyr::case_when(grepl(course_name, pattern = 'Next') ~ as.numeric(date - min(date), units = 'days'), TRUE ~ days),
                `Handicap Index` = dplyr::case_when(grepl(course_name, pattern = 'Next') ~ index, TRUE ~ `Handicap Index`),
                `Predicted Gross` = dplyr::case_when(grepl(course_name, pattern = 'Next') ~ stats::predict(object = gross_lmer,
                                                                                                           newdata = new_df,
                                                                                                           allow.new.levels = T) |>
                                                       as.numeric() %>%
                                                       round(., 0), TRUE ~ `Predicted Gross`),
                `Gross Score` = dplyr::case_when(grepl(course_name, pattern = 'Next') ~ `Predicted Gross`, TRUE ~ `Gross Score`)) |> 
  
  dplyr::group_by(course_name) |> 
  ggplot2::ggplot(aes(x = date, y = `Gross Score`, group = course_name, color = course_name, fill = course_name)) +
  ggplot2::geom_point(size = 5, alpha = 0.7, inherit.aes = T) +
  ggplot2::geom_line(aes(x = date, y = `Gross Score`), color = 'black', alpha = 0.5, size = 1.5, inherit.aes = F) +
  ggplot2::geom_line(aes(x = date, y = `Predicted Gross`), color = 'navy', alpha = 0.7, size = 3, inherit.aes = F) +
  ggplot2::geom_smooth(aes(x = date, y = `Gross Score`, group = course_name, color = course_name, fill = course_name), size = 2, method = 'lm', se = F) +
  ggplot2::labs(title = paste0('LMER-Predicted Gross Scores\n(navy or with text)\nas of ', Sys.Date()),
                color = 'Course') +
  ggplot2::theme_bw() +
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 13),
                 panel.grid.minor = ggplot2::element_blank(),
                 legend.title = ggplot2::element_text(face = 'bold', size = 11),
                 legend.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.key.width = rel(0.4),
                 legend.key.height = rel(0.4),
                 legend.key.spacing.y = rel(0.4),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text.x = ggplot2::element_text(face = 'bold', size = 9, angle = 270, hjust = 0, vjust = 0.5),
                 axis.text.y = ggplot2::element_text(face = 'bold', size = 9)
                 ) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b') +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_text(aes(x = lubridate::as_date(round_date),
                         y = stats::predict(object = gross_lmer,
                                                newdata = new_df,
                                                allow.new.levels = T) |>
                           as.numeric() %>%
                           round(., 0),
                         label = stats::predict(object = gross_lmer,
                                                newdata = new_df,
                                                allow.new.levels = T) |>
                           as.numeric() %>%
                           round(., 0)),
                     inherit.aes = F, size = 3, color = 'black', hjust = -0.1)
```

##### Actual Gross vs Predicted Gross (performance vs prediction)

```{r PlotActualVsPredictedGross, include = T, message = F, warning = F, echo = F, render = T}
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1, # include days
    
    `Predicted Gross` = stats::predict(
      gross_lmer,
      re.form = NULL)) |> # add the lmer's predicted Gross Scores
  
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Predicted Gross`,
                  `Net Score`) |> 
  
  dplyr::mutate(residual = `Gross Score` - `Predicted Gross`) |> 
  ggplot2::ggplot(aes(x = date,
                      y = residual,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Performance vs Prediction\nfrom ',
                               scores |> 
                                 dplyr::ungroup() |> 
                                 dplyr::arrange(date) |>  
                                 dplyr::select(date) |> 
                                 unlist() |> lubridate::as_date() |> 
                                 dplyr::first() |> as.character(),
                               ' - present\nas of ',
                               Sys.Date()),
                               
                x = 'date',
                y = 'Actual Gross Score - Predicted Gross Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8),
                 legend.key.height = rel(0.4),
                 legend.key.width = rel(0.4),
                 legend.key.spacing.y = rel(0.4)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = date, y = residual), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = date, y = residual), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = date, y = residual, label = `Handicap Index`),
                     size = 3, color = 'black')
```

This plot of residuals reveals the `Actual Gross Score` relative to the `Predicted Gross Score` over time, color-coded by `course`, and annotated by `Handicap Index` at the time of the round.

+ the navy blue line represents the dividing line between over/under performing where:

  + scores **above** the line = I performed **worse** than the model's prediction
  + scores **below** the line = I performed **better** than the model's prediction
  
+ `Randolph North`, `Silverbell`, and `Dell Urich` each have lines representing the trend of actual `Gross Score`s compared to predicted `Gross Score`s at each respective course

  + I more often score better/lower at `Randolph North` than the model predicts, though, on average, these are closest to the model's predictions
  
    + This might reveal that these rounds are contributing more weight to the model if they are not simply more reflective of the overall trend
    
    + This could also reveal that I score more consistently at this course than others
    
    + This could also mean that, given the downward trend, the course is easier than ratings suggest
    
  + At `Silverbell` and `Randolph North`, I have been outperforming the model and scoring better over time
    
  + The variability at `Dell Urich` is substantial, with one large outlier overperformance (~ **-15**), and one moderate outlier underperformance (~ **+6**) re-shaping the slope in the opposite direction: I have been getting worse at `Dell Urich` over time
  
    + Even with more subsequent sample, this could reveal that I struggle to shoot low `Gross Score`s at `Dell Urich`, despite its easier course rating, and any effect of time
    
    + Other latent variables may contribute to this variability, such as course/weather/event conditions

```{r PlotActualNetVsPredictedGross, include = F, message = F, warning = F, echo = F, render = F}
#### Actual Net vs Predicted Gross (skill-adjusted performance vs prediction)

scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1, # include days
    
    `Predicted Gross` = stats::predict(
      gross_lmer,
      re.form = NULL)) |> # add the lmer's predicted Gross Scores
  
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Predicted Gross`,
                  `Net Score`) |> 
  
  dplyr::mutate(residual = `Predicted Gross` - `Net Score`) |> 
  ggplot2::ggplot(aes(x = date,
                      y = residual,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Performance vs Prediction\nfrom ',
                               scores |> 
                                 dplyr::ungroup() |> 
                                 dplyr::arrange(date) |>  
                                 dplyr::select(date) |> 
                                 unlist() |> lubridate::as_date() |> 
                                 dplyr::first() |> as.character(),
                               ' - present\nas of ',
                               Sys.Date()),
                x = 'date',
                y = 'Predicted Gross Score - Net Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = date, y = residual), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = date, y = residual), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = date, y = residual, label = `Handicap Index`),
                     size = 3, color = 'black')
```

```{r Interpretation text for Actual Net vs Predicted Gross, include = F, message = F, warning = F, echo= F}
# Relative to the previous plot, this plot of residuals:
# 
# + shifts the previous plot upward
# 
# + inverts it about the x-axis
# 
# + rotates it slightly about the origin
# 
# It shows the `Actual Net Score` relative to the `Predicted Gross Score` over time, color-coded by `course`, and annotated by `Handicap Index` at the time of the round.
# 
# `Net Score` is roughly `Gross Score` - `Handicap Index`.
# 
# + the navy blue line represents the dividing line between over/under performing where:
# 
#   + scores **below** the line = I performed **worse** than the model's prediction
#   + scores **above** the line = I performed **better** than the model's prediction
#   
# + `Randolph North`, `Silverbell`, and `Dell Urich` each have lines representing the trend of actual `Net Score`s compared to `Predicted Gross Score`s at each respective course
# 
#   + I more often score better/lower at `Randolph North` than the model predicts, particularly over time, given my handicap; however, on average, these are closest to the model's predictions than other courses
#   
#     + This reveals that these rounds could be giving more weight to the model
#     
#     + This could also reveal that I more consistently, if slightly, outscore the model at this course, even given my `Handicap Index`
#     
#     + This could also mean that the course is easier than ratings suggest
#     
#     + My instinct is that my `Handicap Index` was overestimated early on in this time series; it was high, and I frequently played `Randolph North` around then, and shot lower scores, directing the trend downward
#     
#   + The variability at `Dell Urich` is substantial, with one large outlier overperformance (~ **-15**), and one moderate outlier underperformance (~ **+6**) re-shaping the slope in the opposite direction (positive as opposed to a negative slope, like `Silverbell` and `Randolph North`)
#   
#     + Even with more subsequent sample, this could reveal that I struggle to shoot low `Gross Score`s at `Dell Urich`, despite its easier course rating
#     
#       + See the plot below for more insight
#     
#     + Other latent variables may contribute to this variability, such as course/weather/event conditions
```

```{r PlotGrossScoreVsCourseRating, include = F, warning = F, message = F, echo = F, render = F}
#### Actual Gross vs Course Rating (performance vs course difficulty)
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1) |>  # include days
  
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Net Score`) |> 
  ggplot2::ggplot(aes(y = `Gross Score`,
                      x = course_rating,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Gross Score vs Course Difficulty\nfrom ',
                               scores |>
                                 dplyr::ungroup() |>
                                 dplyr::arrange(date) |>
                                 dplyr::select(date) |>
                                 unlist() |> lubridate::as_date() |>
                                 dplyr::first() |> as.character(),
                               ' - present\nas of ',
                               Sys.Date()),
                x = 'Course Rating',
                y = 'Gross Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = course_rating, y = `Gross Score`), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = course_rating, y = `Gross Score`), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = course_rating, y = `Gross Score`,
                         label = `Handicap Index`),
                     size = 3, color = 'black')
```

```{r Interpretation text For Actual Gross vs Course Rating, include = F, message = F, warning = F, echo = F}
# This definitely shows that I struggle at `Dell Urich`-- independent of time, my `Gross Score`s at `Dell Urich` are roughly similar to other courses despite its easier rating-- this would be even more evident without the substantial `Gross Score` **72** outlier.
# 
# + Interestingly, I have scored better at longer/more difficult tees at multiple courses.
# 
# + Removing the effect of time/improved skill, and the wildly underrated `Arizona National` rating, this would otherwise capture the general trend and logic that **higher `course ratings` correlate to higher `Gross Score`s**
```

```{r PlotGrossScoreVsHandicapIndex, include = T, message = F, warning = F, echo = F, render = T}
#### Actual Gross vs Handicap Index (performance vs skill-level)
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1) |> # include days
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Net Score`) |>  
  ggplot2::ggplot(aes(x = `Handicap Index`,
                      y = `Gross Score`,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Gross Score vs Handicap Index\nfrom ',
                               scores |>
                                 dplyr::ungroup() |>
                                 dplyr::arrange(date) |>
                                 dplyr::select(date) |>
                                 unlist() |> lubridate::as_date() |>
                                 dplyr::first() |> as.character(),
                               ' - present\nas of ',
                               Sys.Date()),
                x = 'Handicap Index',
                y = 'Gross Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = `Handicap Index`, y = `Gross Score`), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = `Handicap Index`, y = `Gross Score`), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = `Handicap Index`, y = `Gross Score`, label = `Handicap Index`),
                     size = 3, color = 'black')
```

```{r Interpretation text for Actual Gross vs Handicap Index, include = F, warning = F, message = F, echo = F}
# This also supports the ideas that, independent of time and `Handicap Index`, I struggle at `Dell Urich` because of the high `Gross Score`s at low `Handicap Index`:
# 
# + Removing the outlier at a **`Handicap Index` of 14**, the `Dell Urich` trend still doesn't reverse, though the overall trend does-- independent of time and one outlier/corrective round, I perform worse at a course with a lower `Handicap Index`.
```

```{r PlotGrossScoreVsHandicapIndexWithout72, include = F, message = F, warning = F, echo = F, render = F}
### Actual Gross vs Handicap Index, 72 removed (performance vs skill-level, removing outlier)
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1) |> # include days
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Net Score`) |>  
  dplyr::filter(!grepl(date, pattern = '2025-08-03')) |> 
  ggplot2::ggplot(aes(x = `Handicap Index`,
                      y = `Gross Score`,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Gross Score vs Handicap Index\nfrom ',
                               scores |>
                                 dplyr::ungroup() |>
                                 dplyr::arrange(date) |>
                                 dplyr::select(date) |>
                                 unlist() |> lubridate::as_date() |>
                                 dplyr::first() |> as.character(),
                               ' - present\n(removing outlier 72)\nas of ',
                               Sys.Date()),
                x = 'Handicap Index',
                y = 'Gross Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = `Handicap Index`, y = `Gross Score`), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = `Handicap Index`, y = `Gross Score`), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = `Handicap Index`, y = `Gross Score`, label = `Handicap Index`),
                     size = 3, color = 'black')
```


```{r PlotNetScoreVsCourseDifficulty, include = F, warning = F, message=F, echo = F, render = F}
#### Actual Net vs Course Rating (skill-adjusted performance vs course difficulty)
scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1
    ) |> # add the lmer's predicted Gross Scores
  
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Net Score`) |> 
  ggplot2::ggplot(aes(y = `Net Score`,
                      x = course_rating,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Net Score vs Course Difficulty\nfrom ',
                               scores |>
                                 dplyr::ungroup() |>
                                 dplyr::arrange(date) |>
                                 dplyr::select(date) |>
                                 unlist() |> lubridate::as_date() |>
                                 dplyr::first() |> as.character(),
                               ' - present\nas of ',
                               Sys.Date()),
                x = 'Course Rating',
                y = 'Net Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = course_rating, y = `Net Score`), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = course_rating, y = `Net Score`), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = course_rating, y = `Net Score`, label = `Handicap Index`),
                     size = 3, color = 'black')
```

```{r PlotNetScoreVsCourseRatingWithout72AndCombos, include = F, message = F, warning= F, echo = F, render = F}
## Actual Net vs Course Rating without 72 and Combo Tees

scores_sum |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    course_name = gsub(date_course,
                       pattern = '[0-9]|\\-|\\\n|\\.',
                       replacement =  ''), # extract course name
    
    days = as.numeric(date - min(date),
                      units = 'days') + 1 # include days
    ) |> # add the lmer's predicted Gross Scores
  dplyr::filter(!(grepl(course_name, pattern = 'Dell') &
                   course_rating != 67.8) &
                  !(grepl(course_name, pattern = 'Rand') &
                      course_rating != 69.8)) |> 
  dplyr::distinct(course_name, 
                  course_rating, 
                  date, days, 
                  `Gross Score`, 
                  `Handicap Index`,
                  `Net Score`) |> 
  dplyr::filter(!grepl(date, pattern = '2025-08-03')) |> 
  ggplot2::ggplot(aes(y = `Net Score`,
                      x = course_rating,
                      group = course_name,
                      color = course_name,
                      fill = course_name)) +
  ggplot2::geom_point(alpha = 0.5, size = 4) +
  ggplot2::labs(title = paste0('Net Score vs Course Difficulty\nfrom ',
                               scores |>
                                 dplyr::ungroup() |>
                                 dplyr::arrange(date) |>
                                 dplyr::select(date) |>
                                 unlist() |> lubridate::as_date() |>
                                 dplyr::first() |> as.character(),
                               ' - present\n(removing outlier 72 and long combo rounds)\nas of ',
                               Sys.Date()),
                x = 'Course Rating',
                y = 'Net Score',
                color = 'Course') +
  ggplot2::theme_bw()+
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 9),
                 legend.title = ggplot2::element_text(face = 'bold', size = 9),
                 legend.text = ggplot2::element_text(face = 'bold', size = 8)) +
  ggplot2::guides(fill = 'none') +
  ggplot2::geom_smooth(aes(x = course_rating, y = `Net Score`), 
                       method= 'lm', se = F, size = 2.5, alpha = 0.5)+
  ggplot2::geom_smooth(aes(x = course_rating, y = `Net Score`), 
                       method = 'lm', se = F, inherit.aes = F, size = 2.5,
                       alpha = 0.5, color = 'navy') +
  ggplot2::geom_text(aes(x = course_rating, y = `Net Score`, label = `Handicap Index`),
                     size = 3, color = 'black')
```