---
title: "Scorecard Update"
author: "Erik Larsen"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    fig_width: 10
    fig_height: 10
    code_folding: hide
  pdf_document:
    fig_width: 10
    fig_height: 10
    latex_engine: xelatex
  md_document:
    variant: gfm
---

```{r setup, eval = T, include = T, echo = F, message = F, warning = F}
# set chunks, absolute path to the db
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 10,
  dev = c("png", "pdf"),
  fig.path = "../figures/scorecard_update/"
)

# make sure the connection is to the actual db, not a temp; get to the repo root
real_db <- fs::path_abs("inst/extdata/golf.duckdb")
# real_db <- fs::path_abs(paste0(getwd(), "../../../inst/extdata/golf.duckdb"))
```

```{r Refresh dev tables, include = T, eval = T, message =F, warning = F, echo = F}
# refresh the dev tables from current production tables
con <- golf::get_db_connection(db_path = real_db)
golf::refresh_dev_tables(db_path = real_db)
```


## Overview

This markdown shows the data logging process of each round, and shows performance trends and metric averages

## Set-Up Environment {.tabset .tabset-pills .tabset-fade}

### Attach Packages

```{r Attach Packages, include = T, message = F, warning = F, eval = T}
library(golf)
library(tidyverse)
library(DBI)
library(duckdb)
```

## Record New Scorecard {.tabset .tabset-pills .tabset-fade}

### Input the Scores Data

```{r Annotate the new data, include = T, message = F, warning = F, echo = T, eval = T}
# required inputs to fill out the scorecard

round_course <- 'Randolph North'
round_date <- '2026-06-07'
round_tees <- 'white'

hole_scores <- c(4, 3, 6, 5, 4, 3, 3, 4, 5,
                 5, 3, 5, 3, 6, 4, 4, 5, 5)

FIRs <- c(1, rep(0, 5), 1, 0, 0,
          1, 0, 0, 1, rep(0, 5))

GIRs <- c(0, 1, 0, 0, 1, 0, 1, 0, 0,
          0, 1, 0, 1, 0, 0, 1, 0, 0) 

putts_rec <- c(1, 1, 2, 2, 2, 1, 1, 1, 1,
               2, 2, 2, 1, 2, 2, 1, 2, 1)

chips_rec <- c(1, 0, 1, 1, 0, 1, 0, 2, 2,
               1, 0, 1, 0, 1, 1, 1, 1, 1)

penalties_rec <- c(rep(0, 18))

tee_clubs <- c('D', 'D', 'D', 'D', 'D', 'PW', '4', '7', 'D',
               'D', '7', 'D', 'D', 'D', '8', 'D', 'D', 'D')

index <- 11.0
```

### Specify Course and Tees

```{r Specify the Course and Tees, include = T, message = F, warning = F, eval = T}
# get the scorecard for the new round, ensuring hole-by-hole scores are filled
if ( length(hole_scores) > 0 ) {
 Card <- golf::get_course(course = round_course, date = round_date, tees = round_tees) 
}
```

### Get Scoring Metrics

```{r Get Scoring Metrics, include = T, message = F, warning = F, eval = T}
# fill the scorecard for the new round, ensuring hole-by-hole scores are filled
if ( length(hole_scores) > 0 ) {
 Card <- golf::log_score(Scorecard = Card,
                       hole_by_hole = hole_scores,
                       GHIN = 10526424,
                       index = index,
                       FIR = FIRs,
                       GIR = GIRs,
                       putts = putts_rec,
                       chips = chips_rec,
                       penalties = penalties_rec,
                       tee_club = tee_clubs) 
}
```

## Update the db {.tabset .tabset-pills .tabset-fade}

### Update the Players Table

```{r Update the players table out, include = T, message = F, warning = F, echo = T, eval = F}
con <- golf::get_db_connection()

# if the logged data is newer than the last logged round in the 'rounds' table, 
# update the 'players' table

if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM rounds ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &
     
     length(hole_scores) > 0
     ) {

  DBI::dbAppendTable(conn = con,
                   name = 'players',
                   value = players <- Card |> 
                     dplyr::select(GHIN, index, date) |> 
                     dplyr::distinct() |> 
                     dplyr::rename(handicap_index = index) |> 
                     dplyr::mutate(date = as.character(date))
                   )
  
}
```

```{r Update the players table in, include = T, message = F, warning = F, echo = F, eval = F}
con <- golf::get_db_connection()

# if the logged data is newer than the last logged round in the 'rounds' table, 
# update the 'players' table

if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM rounds ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &
     
     length(hole_scores) > 0
     ) {

  DBI::dbAppendTable(conn = con,
                   name = 'dev_players',
                   value = players <- Card |> 
                     dplyr::select(GHIN, index, date) |> 
                     dplyr::distinct() |> 
                     dplyr::rename(handicap_index = index) |> 
                     dplyr::mutate(date = as.character(date))
                   )
  
}
```


### Update the Courses Table

```{r Update the courses table out, include = T, message = F, warning= F, eval = F, echo = T}
con <- golf::get_db_connection()

# if the logged data is newer than the last logged round in the 'rounds' table, 
# update the 'courses' table

if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM rounds ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &
     
     length(hole_scores) > 0
     ) {
  DBI::dbAppendTable(conn = con,
                   name = 'courses',
                   value = course <- Card |> 
                     dplyr::select(course, tees, to_par, slope, course_rating, hole, yds, par, hole_handicap) |> 
                     dplyr::distinct() |> 
                     dplyr::rename(course_name = course) |> 
                     dplyr::mutate(hole = gsub(hole, 
                                               pattern = 'hole_',
                                               replacement = '') |> as.numeric())
                   )
}
```

```{r Update the courses table in, include = T, message = F, warning = F, eval = F, echo = F}
con <- golf::get_db_connection()

# if the logged data is newer than the last logged round in the 'rounds' table, 
# update the 'courses' table

if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM rounds ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &
     
     length(hole_scores) > 0
     ) {
  DBI::dbAppendTable(conn = con,
                   name = 'dev_courses',
                   value = course <- Card |> 
                     dplyr::select(course, tees, to_par, slope, course_rating, hole, yds, par, hole_handicap) |> 
                     dplyr::distinct() |> 
                     dplyr::rename(course_name = course)  |> 
                     dplyr::mutate(hole = gsub(hole, 
                                               pattern = 'hole_',
                                               replacement = '') |> as.numeric())
                   )
}
```


### Update the Rounds Table

```{r Update the rounds table out, include= T, message = F, warning = F, eval = F, echo = T}
con <- golf::get_db_connection()

# if the logged data is newer than the last logged round in the 'rounds' table, 
# update the 'rounds' table

if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM rounds ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &
     
     length(hole_scores) > 0
     ) {
  DBI::dbAppendTable(conn = con,
                   name = 'rounds',
                   value = Card |> 
                     dplyr::select(-to_par, -slope, -course_rating, -yds, -par) |> 
                     dplyr::distinct() |>
                     dplyr::rename(handicap_index = index) |> 
                     dplyr::rename(course_name = course) |> 
                     dplyr::mutate(date = as.character(date))  |> 
                     dplyr::mutate(hole = gsub(hole, 
                                               pattern = 'hole_',
                                               replacement = '') |> as.numeric())
                   )
}
```

```{r Update the rounds table in, include = T, message = F, warning = F, eval = F, echo = F}
con <- golf::get_db_connection()

# if the logged data is newer than the last logged round in the 'rounds' table, 
# update the 'rounds' table

if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM rounds ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &
     
     length(hole_scores) > 0
     ) {
  DBI::dbAppendTable(conn = con,
                   name = 'dev_rounds',
                   value = Card |> 
                     dplyr::select(-to_par, -slope, -course_rating, -yds, -par) |> 
                     dplyr::distinct() |>
                     dplyr::rename(handicap_index = index) |> 
                     dplyr::rename(course_name = course) |> 
                     dplyr::mutate(date = as.character(date))  |> 
                     dplyr::mutate(hole = gsub(hole, 
                                               pattern = 'hole_',
                                               replacement = '') |> as.numeric())
                   )
}
```


### Get Club Metrics df

```{r Get the Club Metrics df, include = T, message = F, warning = F, echo = T, eval = T}
# create a dataframe, specifying the shape for tracked shots on each hole
  # -> all strokes from off the green

club_metrics_df <- golf::get_tracked_shots_data_shape(round_date = round_date) |> 
  dplyr::arrange(hole)
```

### Annotate Club Metrics

```{r Annotate the New Club Metrics, include = T, message = F, warning = F, echo = T, eval = T}
# manually annotate from Garmin Golf App log
club_choice <- c(
  'D', 'GW', 'P',
  'D', 'GW',
  'D', '5', '5', 'PW',
  'D', '5', 'PW',
  'D', '9',
  'PW', 'PW',
  '4', 'PW',
  '7', 'GW', 'PW',
  'D', '5', '7', 'PW',
  
  'D', 'GW', 'LW',
  '7',
  'D', 'GW', 'P',
  'D', '4',
  'D', '4', '6', 'PW',
  '8', 'SW',
  'D', '3W', 'PW',
  'D', 'PW', 'SW',
  'D', '5', 'GW', 'LW'
)

dist_to_target <- c(
  270, 34, 8,
  270, 48,
  270, 205, 189, 8,
  270, 189, 16,
  270, 148,
  129, 30,
  220, 130,
  173, 25, 12,
  270, 209, 46, 21,
  
  270, 112, 18,
  185,
  270, 118, 9,
  270, 208,
  270, 220, 191, 13,
  168, 13,
  270, 233, 15,
  270, 148, 27,
  270, 206, 105, 11
)

yds <- c(
  310, 27, 8,
  308, 42,
  245, 71, 182, 6,
  241, 173, 13,
  281, 147,
  146, 24,
  224, 130,
  166, 12, 9,
  231, 188, 49, 23,
  
  288, 106, 13,
  173,
  267, 110, 9,
  256, 208,
  118, 100, 188, 13,
  159, 14,
  263, 242, 9,
  222, 130, 27,
  200, 101, 102, 7
)
lie_type <- c(
  'tee', 'fairway', 'fairway',
  'tee', 'rough',
  'tee', 'sand', 'fairway', 'fairway',
  'tee', 'rough', 'fairway',
  'tee', 'rough',
  'tee', 'rough',
  'tee', 'fairway',
  'tee', 'rough', 'rough',
  'tee', 'fairway', 'rough', 'rough',
  
  'tee', 'fairway', 'sand',
  'tee',
  'tee', 'rough', 'fairway',
  'tee', 'fairway',
  'tee', 'rough', 'rough', 'fairway',
  'tee', 'rough',
  'tee', 'rough', 'rough',
  'tee', 'fairway','sand',
  'tee', 'fairway', 'fairway', 'sand'
)

target_status <- c(
  'yes', 'no', 'yes',
  'no', 'yes',
  'no', 'no', 'no', 'yes',
  'no', 'yes', 'yes',
  'no', 'yes',
  'no', 'yes',
  'yes', 'yes',
  'no', 'no', 'yes',
  'no', 'no', 'yes', 'yes',
  
  'yes', 'no', 'yes',
  'yes',
  'no', 'no', 'yes',
  'yes', 'yes',
  'no', 'no', 'no', 'yes',
  'no', 'yes',
  'no', 'no', 'yes',
  'no', 'no', 'yes',
  'no', 'no', 'no', 'yes'
)

location <- c(
  'on_target', 'short', 'on_target',
  'right', 'on_target',
  'right', 'short', 'short', 'on_target',
  'right', 'on_target', 'on_target',
  'left', 'on_target',
  'left', 'on_target',
  'on_target', 'on_target',
  'right', 'short', 'on_target',
  'right', 'right', 'on_target', 'on_target',
  
  'on_target', 'right', 'on_target',
  'on_target', 
  'right', 'short', 'on_target',
  'on_target', 'on_target',
  'left', 'short', 'long', 'on_target',
  'short', 'on_target',
  'right', 'long', 'on_target',
  'right', 'left', 'on_target',
  'right', 'short', 'left', 'on_target'
)

type_of_shot <- c(
  'tee', 'choked', 'chip',
  'tee', 'chip',
  'tee', 'fwbunker', 'full', 'chip',
  'tee', 'punch', 'chip',
  'tee', 'full',
  'tee', 'chip',
  'tee', 'full',
  'tee', 'chip', 'chip',
  'tee', 'full', 'chip', 'chip',
  
  'tee', 'choked', 'gsbunker',
  'tee',
  'tee', 'full', 'chip',
  'tee', 'full',
  'tee', 'punch', 'full', 'chip',
  'tee', 'chip',
  'tee', 'full', 'chip',
  'tee', 'full', 'gsbunker',
  'tee', 'full', 'choked', 'gsbunker'
)
```

### Get Shot Metrics

```{r Gather shot metrics data, include = T, message = F, warning = F, echo = T, eval = F}
con <- golf::get_db_connection()

# if the data is newer than the last round in the 'club_metrics' table, append
  # the new annotations (expands from 18 rows by the number determined from the 
  # get_tracked_shots_data_shape function)

if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM club_metrics ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &
     
     length(hole_scores) > 0
) {
  length(club_choice)
  club_metrics <- golf::harmonize_club_metrics(club_metrics = club_metrics_df,
                                               club_choice = club_choice,
                                               distance_to_target = dist_to_target,
                                               distance_traveled = yds,
                                               lie_type = lie_type,
                                               target_status = target_status,
                                               location = location,
                                               type_of_shot = type_of_shot
                                               )
  club_metrics <- club_metrics |> 
    dplyr::mutate(dplyr::across(c(dplyr::contains("yds")), ~as.numeric(.x)))
  head(club_metrics)
}

club_metrics_df |> dplyr::select(tracked_shots) |> dplyr::mutate(sum(tracked_shots))
```

```{r Gather shot metrics data quiet, include = T, message = F, warning = F, echo = F, eval = T}
con <- golf::get_db_connection()

# if the data is newer than the last round in the 'club_metrics' table, append
  # the new annotations (expands from 18 rows by the number determined from the 
  # get_tracked_shots_data_shape function)

if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM club_metrics ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &
     
     length(hole_scores) > 0
) {
  length(club_choice)
  club_metrics <- golf::harmonize_club_metrics(club_metrics = club_metrics_df,
                                               club_choice = club_choice,
                                               distance_to_target = dist_to_target,
                                               distance_traveled = yds,
                                               lie_type = lie_type,
                                               target_status = target_status,
                                               location = location,
                                               type_of_shot = type_of_shot
                                               )
  club_metrics <- club_metrics |> 
    dplyr::mutate(dplyr::across(c(dplyr::contains("yds")), ~as.numeric(.x)))
  head(club_metrics)
}

club_metrics_df |> dplyr::select(tracked_shots) |> dplyr::mutate(sum(tracked_shots))
```


### Update the Club Metrics Table

```{r Update the club metrics table out, include = T, message = F, warning = F, eval = F, echo = T}
con <- golf::get_db_connection()

# if the data is newer than the last round in the 'club_metrics' table, append
  # the new data to the table

if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM club_metrics ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &
     
     length(hole_scores) > 0
     ) {
  DBI::dbAppendTable(conn = con,
                   name = 'club_metrics',
                   value = club_metrics |> 
                     dplyr::mutate(date = as.character(date))
                   )
}
```

```{r Update the club metrics table in, include = T, message = F, warning = F, eval = F, echo = F}
con <- golf::get_db_connection()

# if the data is newer than the last round in the 'club_metrics' table, append
  # the new data to the table

if ( DBI::dbGetQuery(conn = con, statement = paste0("SELECT DISTINCT date FROM club_metrics ORDER BY date DESC LIMIT 1;")) |> 
     dplyr::distinct(date) |> 
     unlist() %>% 
     lubridate::as_date(.) |> 
     as.character() < round_date &&
     
     length(hole_scores) > 0
     ) {
  
  DBI::dbAppendTable(conn = con,
                   name = 'dev_club_metrics',
                   value = club_metrics |> 
                     dplyr::mutate(date = as.character(date))
                   )
}
```


```{r Clear Environment, include = T, message = F, warning = F, eval = T}
# clean the global environment
rm(list = ls()[which(grepl(ls(), pattern= 'con|round_course|round_date|index|real_db')==F)])
```

## Summarize Metrics {.tabset .tabset-pills .tabset-fade}

### Gather and Format

Gather and format from the database

```{r Summarize Stroke Metrics out, include = T, message = F, warning = F, echo = T, eval = F}
con <- golf::get_db_connection()

# get the hole-by-hole scores from each round in the database

  # join the hole-by-hole scores from the 'rounds' table to the 'courses' table
    # need each hole's par rating 
    # need each course's course_rating from the 'courses' table
  
  # join the 'rounds' and 'courses' tables to the 'players' table
    # need handicap_index from the 'players' table

scores <- DBI::dbGetQuery(conn = con, statement = paste0(
  "SELECT DISTINCT r.*, c.par, c.course_rating FROM rounds r
  INNER JOIN courses c
  ON c.tees = r.tees
  AND c.course_name = r.course_name
  AND c.hole = r.hole
  INNER JOIN players p
  ON r.GHIN = p.GHIN
  AND r.handicap_index = p.handicap_index
  AND r.date = p.date;"
)) |> 
  dplyr::mutate(date = lubridate::as_date(date)) |> # convert strings to date's
  dplyr::relocate(par, .after = hole) |> 
  dplyr::relocate(course_rating, .after = tees) |>
  dplyr::group_by(date) |> 
  dplyr::arrange(desc(date), hole) |> 
  dplyr::ungroup()
```

```{r Summarize Stroke Metrics in, include = T, message = F, warning = F, echo = F, eval = T}
con <- golf::get_db_connection()

# get the hole-by-hole scores from each round in the database

  # join the hole-by-hole scores from the 'rounds' table to the 'courses' table
    # need each hole's par rating 
    # need each course's course_rating from the 'courses' table
  
  # join the 'rounds' and 'courses' tables to the 'players' table
    # need handicap_index from the 'players' table

scores <- DBI::dbGetQuery(conn = con, statement = paste0(
  "SELECT DISTINCT r.*, c.par, c.course_rating FROM dev_rounds r
  INNER JOIN dev_courses c
  ON c.tees = r.tees
  AND c.course_name = r.course_name
  AND c.hole = r.hole
  INNER JOIN dev_players p
  ON r.GHIN = p.GHIN
  AND r.handicap_index = p.handicap_index
  AND r.date = p.date;"
)) |> 
  dplyr::mutate(date = lubridate::as_date(date)) |> # convert strings to date's
  dplyr::relocate(par, .after = hole) |> 
  dplyr::relocate(course_rating, .after = tees) |>
  dplyr::group_by(date) |> 
  dplyr::arrange(desc(date), hole) |> 
  dplyr::ungroup()
```


```{r Summarize Club Metrics out, include = T, message = F, warning = F, echo = T, eval = F}
con <- golf::get_db_connection()

# get stroke metrics from the 'club_metrics' table

stroke_quality <- DBI::dbGetQuery(conn = con, statement = paste0(
  "SELECT DISTINCT * FROM club_metrics;"
)) |> 
  dplyr::mutate(date = lubridate::as_date(date)) |> # convert strings to date's
  dplyr::group_by(date) |> 
  dplyr::arrange(desc(date), hole, stroke) |> 
  dplyr::ungroup()
```



```{r Summarize Club Metrics in, include = T, eval = T, message = F, warning = F, echo = F}
con <- golf::get_db_connection()

# get stroke metrics from the 'club_metrics' table

stroke_quality <- DBI::dbGetQuery(conn = con, statement = paste0(
  "SELECT DISTINCT * FROM dev_club_metrics;"
)) |> 
  dplyr::mutate(date = lubridate::as_date(date)) |> # convert strings to date's
  dplyr::group_by(date) |> 
  dplyr::arrange(desc(date), hole, stroke) |> 
  dplyr::ungroup()
```


```{r Validate dev updates, include = T, eval = F, message = F, warning = F, echo = F}
con <- golf::get_db_connection(db_path = real_db)
golf::validate_dev_tables(db_path = real_db)
```

```{r Promote dev to prod, include = T, eval = F, message = F, warning = F, echo = F}
con <- golf::get_db_connection(db_path = real_db)
golf::promote_dev_to_production(db_path = real_db)
```

```{r Pass Data Through Skill Pipeline, include = T, eval = F, message = F, warning = F, echo = F}
con <- golf::get_db_connection(db_path = real_db)
golf::run_skill_pipeline(db_path = real_db)
```

```{r Overwrite PowerBI CSVs, include = T, eval = T, message = F, warning = F, echo = F}
# source('C:/Users/Erik/Desktop/Programming/R/Sports/golf/dev/local/overwrite_csvs.R')
```


### Compute Metrics

Compute standard metrics

```{r Compute Advanced Metrics 1, include = T, warning = F, message = F, eval = T}
# define metrics
scores_sum <- scores |>
  dplyr::mutate(date_course = paste0(date,
                                     '\n',
                                     course_name, '\n',
                                     handicap_index),
                chips = dplyr::case_when(
                  grepl(date, pattern = '07-13') ~ NA_real_, TRUE ~ chips),
                `chips+putts` = chips+putts,
                FIR_opps = dplyr::case_when(par > 3 ~ 1, TRUE ~ NA),
                `Iron FIRs` = dplyr::case_when(par > 3 &
                                                 grepl(tee_club, pattern = '4|5') &
                                                 FIR == 1 ~ 1,
                                               TRUE ~ 0),
                `Iron FIR opps` = dplyr::case_when(par > 3 &
                                                     grepl(tee_club, pattern = '4|5') ~ 1,
                                                   TRUE ~ 0),
                `Driver FIRs` = dplyr::case_when(par > 3 &
                                                   tee_club == 'D' &
                                                   FIR == 1 ~ 1,
                                                 TRUE ~ 0),
                `Driver FIR opps` = dplyr::case_when(par > 3 &
                                                     tee_club == 'D' ~ 1,
                                                   TRUE ~ 0),
                `Par 3 GIRs` = dplyr::case_when(par == 3 & 
                                                  GIR == 1 ~ 1,
                                                TRUE ~ 0),
                greenie_putts = dplyr::case_when(GIR == 1 ~ putts, TRUE ~ NA_real_),
                updown_conv = dplyr::case_when(GIR == 0 &
                                                 par == gross ~ 1,
                                               TRUE ~ 0),
                updown_opps = dplyr::case_when(GIR == 0 &
                                                chips > 0 ~ 1,
                                              TRUE ~ 0)
                ) |> 
  dplyr::rename(`Handicap Index` = handicap_index)

# summarize by round
scores_sum <- scores_sum |> 
  dplyr::group_by(date, date_course, course_rating, `Handicap Index`) |> 
  dplyr::summarize(
                   FIRs = sum(FIR, na.rm = F),
                   `Iron FIRs` = sum(`Iron FIRs`, na.rm = T),
                   `Iron FIR%` = round(((sum(`Iron FIRs`, na.rm = T)/sum(`Iron FIR opps`, na.rm = T))*100), 1),
                   `Driver FIRs` = sum(`Driver FIRs`, na.rm = T),
                   `Driver FIR%` = round(((sum(`Driver FIRs`, na.rm = T)/sum(`Driver FIR opps`, na.rm = T))*100), 1),
                   `FIR%` = round((sum(FIRs, na.rm = T)/sum(FIR_opps, na.rm = T))*100, 1),
                   GIRs = sum(GIR, na.rm = F),
                   `Par 3 GIRs` = sum(`Par 3 GIRs`, na.rm = T),
                   `GIR%` = round((sum(GIRs, na.rm = T)/18)*100, 1),
                   putts = sum(putts, na.rm = F),
                   `Avg GIR putts` = round(mean(greenie_putts, na.rm = T), 2),
                   chips = sum(chips, na.rm = F),
                   `chips+putts` = sum(`chips+putts`, na.rm = F),
                   `UpDown%` = round(((sum(updown_conv, na.rm = T)/sum(updown_opps, na.rm = T))*100), 1),
                   pars = sum(is_gross_par, na.rm = F),
                   birdies = sum(is_gross_birdie, na.rm = F),
                   bogies = sum(is_gross_bogey, na.rm = F),
                   `doubles+` = sum(is_gross_bogey_worse, na.rm = F),
                   penalties = sum(penalties, na.rm = T),
                   `Gross Score` = mean(tot_gross, na.rm = F),
                   `Net Score` = mean(tot_net, na.rm = F)) %>%
  dplyr::mutate(dplyr::across(c(`Iron FIRs`, `Driver FIRs`,
                                `Iron FIR%`, `Driver FIR%`, `FIR%`),
                              ~dplyr::if_else(is.na(FIRs), NA, .)),
                
                dplyr::across(c(`Par 3 GIRs`, `Avg GIR putts`,
                                `UpDown%`, `GIR%`), 
                              ~dplyr::if_else(is.na(GIRs), NA, .)),
                
                `chips+putts` = dplyr::case_when(is.na(chips) ~ NA_real_,
                                                 TRUE ~ `chips+putts`)) %>% 
  
  dplyr::mutate(
    
    `UpAndDown%` = dplyr::case_when(
      
      grepl(date, pattern = '07-13|09-21') ~ NA, TRUE ~ `UpDown%`),
    
    `Iron FIR%` = dplyr::case_when(`Iron FIR%` == NaN ~ 0.0, TRUE ~ `Iron FIR%`))
```

```{r Compute Advanced Metrics 2, include = T, warning = F, message = F, eval = T}
head(scores_sum |> 
       dplyr::arrange(desc(date)))
```

### View Metrics {.tabset .tabset-pills .tabset-fade}

Separate and view metrics

#### Scoring Metrics

Scores and Handicap

```{r Separate Scoring Metrics, include = T, warning = F, message = F, eval = T}
scoring_metrics <- scores_sum |> 
  dplyr::select(`Handicap Index`, `Gross Score`, `Net Score`)
head(scoring_metrics |> 
       dplyr::arrange(desc(date)))
```

#### Stroke Metrics

In golf, every hole has a `par`-- an average number of strokes taken to get the 
ball in the hole

There are (almost always), three different `par`s on every course: 

+ `par 3`s
+ `par 4`s
+ `par 5`s

A shorthand to determine how a golfer performed across holes is to rate how many 
strokes *relative to par* they were (-1, -2, +1, +2, etc)

These numbers are given names:

+ `0 = par`
+ `-2 = eagle`
+ `-1 = birdie`
+ `+1 = bogey`
+ `+2 = double bogey`

I quantify these below:

```{r Separate Stroke Metrics, include = T, warning = F, message = F, eval = T}
stroke_metrics <- scores_sum |> 
  dplyr::select(`doubles+`, bogies, pars, birdies)
head(stroke_metrics |> 
       dplyr::arrange(desc(date)))
```

#### Around-the-Green Metrics

`Chips`: 
  + strokes around the green taken to get onto the green

`Putts`:
  + strokes taken with the putter on the green
  
`Avg GIR putts`:
  + Average # of putts on holes where the ball was hit on to the green within 2 strokes of par (green in regulation, `GIR`)
  
`UpDown%` (aka `Scramble%`):
  + # of holes without a `GIR` but par was made / 
  # of holes without a `GIR`

```{r Separate Around the Green Metrics, include = T, warning = F, message = F, eval = T}
atg_metrics <- scores_sum |> 
  dplyr::select(chips, `chips+putts`, `UpAndDown%`, putts, `Avg GIR putts`)
head(atg_metrics |> 
       dplyr::arrange(desc(date)))
```

#### Ball Striking Metrics

Approach and tee accuracy

`GIR (green in regulation)`:
  + hole where the ball was hit on to the green within 2 strokes of par
  
`FIR (fairway in regulation)`:
  + hole where the ball was hit on to the fairway from the tee box (only on par 4's and par 5's)
  
`Iron FIR`:
  + hole where an iron was used off the tee for a `FIR`
  
`Driver FIR`:
  + hole where driver was used off the tee for a `FIR`

```{r Separate Ball Striking Metrics, include = T, warning = F, message = F, eval = T}
ball_striking_metrics <- scores_sum |> 
  dplyr::select(GIRs, `GIR%`, `Par 3 GIRs`,
                FIRs, `FIR%`, `Iron FIRs`, `Iron FIR%`,
                `Driver FIRs`, `Driver FIR%`)
head(ball_striking_metrics |> 
       dplyr::arrange(desc(date)))
```


#### Club Metrics

Yardage and accuracy for each club

```{r Separate Stroke Quality Metrics, include = T, warning = F, message = F, echo = F, eval = T}
stroke_quality <- stroke_quality |> 
  # dplyr::filter(grepl(shot_type, pattern = 'full')) |>
  dplyr::mutate(dplyr::across(dplyr::contains("yds"), ~as.numeric(.x))) |> 
  dplyr::mutate(yd_diff = yds_to_target - yds_traveled,
                on_target = dplyr::case_when(on_target == 'yes' ~ 1, TRUE ~ 0))
```

```{r Separate Stroke Quality Metrics Minimum, include = T, warning = F, message = F, echo = F, eval = T}
stroke_quality_min <- stroke_quality |> 
  dplyr::group_by(date, club) |> 
  dplyr::summarize(rd_min_yds_to_target = round(min(yds_to_target), 1),
                   rd_min_yds_traveled = round(min(yds_traveled), 1),
                   rd_min_yd_diff = round(min(yd_diff), 1),
                   n = dplyr::n()) |> 
  dplyr::relocate(n, .after = club)
head(stroke_quality_min |> 
       dplyr::arrange(desc(date)))
```

```{r Separate Stroke Quality Metrics Maximum, include = T, warning = F, message = F, echo = F, eval = T}
stroke_quality_max <- stroke_quality |> 
  dplyr::group_by(date, club) |> 
  dplyr::summarize(rd_max_yds_to_target = round(max(yds_to_target), 1),
                   rd_max_yds_traveled = round(max(yds_traveled), 1),
                   rd_max_yd_diff = round(max(yd_diff), 1),
                   n = dplyr::n()) |> 
  dplyr::relocate(n, .after = club)
head(stroke_quality_max |> 
       dplyr::arrange(desc(date)))
```

```{r Separate Stroke Quality Metrics Avg, include = T, warning = F, message = F, echo = F, eval = T}
full_stroke_quality_avg <- stroke_quality |> 
  dplyr::filter(grepl(shot_type, pattern = 'full|tee')) |> 
  dplyr::group_by(date, club) |> 
  dplyr::summarize(rd_avg_yds_to_target = round(mean(yds_to_target), 1),
                   rd_avg_yds_traveled = round(mean(yds_traveled),1),
                   rd_avg_yd_diff = round(mean(yd_diff),1),
                   rd_avg_accuracy = round((sum(on_target)/dplyr::n())*100, 2),
                   n = dplyr::n()) |> 
  dplyr::full_join(
    stroke_quality |> 
      dplyr::filter(grepl(shot_type, pattern = 'full|tee')) |> 
      dplyr::group_by(date, club, miss_direction) |> 
      dplyr::summarize(rd_club_miss_direction_n = dplyr::n()) |> 
      dplyr::group_by(date, club) |>
      dplyr::mutate(`rd club % miss direction` = round((rd_club_miss_direction_n/sum(rd_club_miss_direction_n))*100, 1))
  ) |> 
  dplyr::relocate(n, .after = club) |> 
  dplyr::relocate(miss_direction, .after = n) |> 
  dplyr::relocate(rd_club_miss_direction_n, .after = miss_direction) |> 
  dplyr::rename(`rd club strokes` = n) |> 
  dplyr::rename(`rd club miss dir` = rd_club_miss_direction_n)
head(full_stroke_quality_avg |> 
       dplyr::arrange(desc(date)))
```

## Plot Metric Summaries {.tabset .tabset-pills .tabset-fade}

### Scoring Metrics

```{r PlotScoringMetrics, include = T, message = F, warning = F, eval = T}
scoring_metrics |> 
  dplyr::mutate(course_rating = dplyr::case_when(grepl(date_course, pattern = 'Sewailo') ~ 68.9, TRUE ~ course_rating),
                `Handicap Index` = `Handicap Index`*4.5) |>
  dplyr::rename(`Course Rating` = course_rating) |> 
  dplyr::group_by(date, date_course, `Handicap Index`) |> 
  tidyr::pivot_longer(cols = c(`Course Rating`:`Net Score`), names_to = 'metric', values_to = 'value', values_drop_na = F) |> 
  ggplot2::ggplot(aes(x = date_course, y = value)) +
  ggplot2::geom_point(aes(x = date, y = value, size = 4, alpha = 0.1,
                          color = factor(metric,
                                         levels = c('Handicap Index', 'Course Rating', 'Gross Score', 'Net Score')),
                          fill = factor(metric,
                                         levels = c('Handicap Index', 'Course Rating', 'Gross Score', 'Net Score')))) +
  ggplot2::geom_line(aes(x = date, y = value, size = 1, alpha = 0.1,
                          color = factor(metric,
                                         levels = c('Handicap Index', 'Course Rating', 'Gross Score', 'Net Score')),
                          fill = factor(metric,
                                         levels = c('Handicap Index', 'Course Rating', 'Gross Score', 'Net Score')))) +
  ggplot2::geom_smooth(aes(x = date, y = value, group = metric,
                           color = factor(metric,
                                          levels = c('Handicap Index', 'Course Rating', 'Gross Score', 'Net Score')),
                           fill = factor(metric,
                                         levels = c('Handicap Index', 'Course Rating', 'Gross Score', 'Net Score'))),
                       alpha = 0.3, method = 'lm') +
  ggplot2::scale_y_continuous(sec.axis = ggplot2::sec_axis(~./4.5, name = 'Handicap Index'))+
  ggplot2::labs(title = paste0('Performance Over Time\n',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::last() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character(),
                               ' - ',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::first() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character()),
                x = 'date',
                y = 'metric',
                color = 'metric'
                ) +
  ggplot2::guides(alpha = 'none', size = 'none', fill = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(panel.grid.minor = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(face = 'bold'),
                 axis.text.y = ggplot2::element_text(face = 'bold'),
                 axis.text.x = ggplot2::element_text(face = 'bold', angle = 0, hjust = 0, vjust = 0),
                 title = ggplot2::element_text(face = 'bold')
                 ) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b')
```

### Stroke Metrics

```{r PlotStrokeMetrics, include = T, message = F, warning = F, eval = T}
stroke_metrics |> 
  tidyr::pivot_longer(cols = c(`doubles+`:birdies), names_to = 'metric', values_to = 'value', values_drop_na = F) |> 
  ggplot2::ggplot(aes(x = date_course, y = value, group = metric, color = metric, fill = metric)) +
  ggplot2::geom_point(aes(x = date, y = value, size = 4, alpha = 0.1), na.rm = T) +
  ggplot2::geom_line(aes(x = date, y = value, size = 1, alpha = 0.1), na.rm = T) +
  ggplot2::geom_smooth(aes(x = date, y = value), alpha = 0.3, method = 'lm') +
  ggplot2::labs(title = paste0('Hole-by-Hole Scores Over Time\n',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::last() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character(),
                               ' - ',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::first() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character()),
                x = 'date',
                y = 'metric',
                color = 'metric', fill = 'metric') +
  ggplot2::guides(alpha = 'none', size = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = 'none',
                 panel.grid.minor = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(face = 'bold'),
                 axis.text.y = ggplot2::element_text(face = 'bold'),
                 axis.text.x = ggplot2::element_text(face = 'bold', angle = 270, hjust = 0, vjust = 0.5),
                 title = ggplot2::element_text(face = 'bold'),
                 strip.text.x.top = ggplot2::element_text(face = 'bold'),
                 strip.background = ggplot2::element_rect(color = 'black', 
                                                          fill = 'white')) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b') +
  ggplot2::facet_wrap(~factor(metric, levels = c('doubles+', 'bogies', 'pars', 'birdies')), nrow = 1)
```

### Around the Green Metrics

```{r PlotAroundTheGreenMetrics, include = T, message = F, warning = F, eval = T}
atg_metrics |> 
  tidyr::pivot_longer(cols = c(chips:`Avg GIR putts`), names_to = 'metric', values_to = 'value', values_drop_na = F) |> 
  ggplot2::ggplot(aes(x = date_course, y = value, group = metric, color = metric, fill = metric)) +
  ggplot2::geom_point(aes(x = date, y = value, size = 4, alpha = 0.1), na.rm = T) +
  ggplot2::geom_line(aes(x = date, y = value, size = 1, alpha = 0.1), na.rm = T) +
  ggplot2::geom_smooth(aes(x = date, y = value), alpha = 0.3, method = 'lm') +
  ggplot2::labs(title = paste0('Around the Green Metrics Over Time\n',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::last() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character(),
                               ' - ',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::first() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character()),
                x = 'date',
                y = 'metric',
                color = 'metric', fill = 'metric') +
  ggplot2::guides(alpha = 'none', size = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = 'none',
                 panel.grid.minor = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(face = 'bold'),
                 axis.text.y = ggplot2::element_text(face = 'bold'),
                 axis.text.x = ggplot2::element_text(face = 'bold', angle = 270, hjust = 0, vjust = 0.5),
                 title = ggplot2::element_text(face = 'bold'),
                 strip.text.x.top = ggplot2::element_text(face = 'bold'),
                 strip.background = ggplot2::element_rect(color = 'black', 
                                                          fill = 'white')) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b') +
  ggplot2::facet_wrap(~factor(metric, levels = c('chips', 'putts', 'chips+putts', 'UpAndDown%', 'Avg GIR putts')), scales = 'free')
```

### Ball Striking Metrics

```{r PlotBallStrikingMetrics, include = T, message = F, warning = F, eval = T, fig.width=8, fig.height = 8}
ball_striking_metrics |> 
  tidyr::pivot_longer(cols = c(GIRs:`Driver FIR%`), names_to = 'metric', values_to = 'value', values_drop_na = F) |> 
  ggplot2::ggplot(aes(x = date_course, y = value, group = metric, color = metric, fill = metric)) +
  ggplot2::geom_point(aes(x = date, y = value, size = 4, alpha = 0.1), na.rm = T) +
  ggplot2::geom_line(aes(x = date, y = value, size = 1, alpha = 0.1), na.rm = T) +
  ggplot2::geom_smooth(aes(x = date, y = value), alpha = 0.3, method = 'lm') +
  ggplot2::labs(title = paste0('Ball Striking Over Time\n',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::last() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character(),
                               ' - ',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::first() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character()),
                x = 'date',
                y = 'metric',
                color = 'metric', fill = 'metric') +
  ggplot2::guides(alpha = 'none', size = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = 'none',
                 panel.grid.minor = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(face = 'bold'),
                 axis.text.y = ggplot2::element_text(face = 'bold'),
                 axis.text.x = ggplot2::element_text(face = 'bold', angle = 270, hjust = 0, vjust = 0.5),
                 title = ggplot2::element_text(face = 'bold'),
                 strip.text.x.top = ggplot2::element_text(face = 'bold'),
                 strip.background = ggplot2::element_rect(color = 'black', 
                                                          fill = 'white')) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b') +
  ggplot2::facet_wrap(~factor(metric,levels = c('Driver FIRs', 'Iron FIRs', 'FIRs',
                                                'Driver FIR%', 'Iron FIR%', 'FIR%',
                                                'GIRs', 'Par 3 GIRs', 'GIR%')), scales = 'free')
```

### Stroke Quality Metrics {.tabset .tabset-pills .tabset-fade}

#### Minima

```{r PlotStrokeQualityMinMetrics, include = T, message = F, warning = F, eval = T, fig.width=11}
stroke_quality_min |> 
  dplyr::ungroup() %>%
  dplyr::mutate(dplyr::across(c(date:n), ~as.character(.x))) |> 
  tidyr::pivot_longer(cols = c(dplyr::contains('yd')), names_to = 'metric', values_to = 'vals') |> 
  dplyr::mutate(metric = dplyr::case_when(grepl(metric, pattern = 'target') ~ 'min. target distance',
                                          grepl(metric, pattern = 'traveled') ~ 'min. shot distance',
                                          grepl(metric, pattern = 'diff') ~ 'min.\ntarget dist. - shot dist.')) |> 
  dplyr::mutate(date = lubridate::as_date(date),
                club = as.character(club),
                n = as.integer(n)) |> 
  ggplot2::ggplot(aes(x = date, y = vals, group = metric, color = club, fill = club)) +
  ggplot2::geom_point(alpha = 0.4, size = 3) +
  ggplot2::geom_line(alpha = 0.4, size = 2) +
  ggplot2::geom_smooth(method = 'lm', se = F) +
  ggplot2::labs(title = 'Stroke Yardage Minima by Club', x = 'date', y = 'value (yards)', fill = 'club') +
  ggplot2::guides(alpha = 'none', size = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text.x = ggplot2::element_text(face = 'bold', size = 7, angle = 270, hjust = 0, vjust = 0.5),
                 legend.position = 'none',
                 strip.background = ggplot2::element_rect(fill = 'white'),
                 strip.text.y.right = ggplot2::element_text(face = 'bold', size = 9),
                 strip.text.x.top = ggplot2::element_text(face = 'bold', size = 10)) + 
  ggplot2::scale_x_date(date_breaks = 'weeks', date_labels = '%b %d') +
  ggplot2::facet_grid(
    
    rows = vars(metric), 
    
    cols = vars(factor(club, levels = c('D', '3W', '4', '5',
                                        '6', '7', '8', '9',
                                        'PW', 'GW', 'SW', 'LW', 'P'))),
                      scales = 'free')
```

#### Maxima

```{r PlotStrokeQualityMaxMetrics, include = T, message = F, warning = F, eval = T, fig.width=11}
stroke_quality_max |> 
  dplyr::ungroup() %>%
  dplyr::mutate(dplyr::across(c(date:n), ~as.character(.x))) |> 
  tidyr::pivot_longer(cols = c(dplyr::contains('yd')), names_to = 'metric', values_to = 'vals') |> 
  dplyr::mutate(metric = dplyr::case_when(grepl(metric, pattern = 'target') ~ 'max. target distance',
                                          grepl(metric, pattern = 'traveled') ~ 'max. shot distance',
                                          grepl(metric, pattern = 'diff') ~ 'max.\ntarget dist. - shot dist.')) |> 
  dplyr::mutate(date = lubridate::as_date(date),
                club = as.character(club),
                n = as.integer(n)) |> 
  ggplot2::ggplot(aes(x = date, y = vals, group = metric, color = club, fill = club)) +
  ggplot2::geom_point(alpha = 0.4, size = 3) +
  ggplot2::geom_line(alpha = 0.4, size = 2) +
  ggplot2::geom_smooth(method = 'lm', se = F) +
  ggplot2::labs(title = 'Stroke Yardage Maxima by Club', x = 'date', y = 'value (yards)', fill = 'club') +
  ggplot2::guides(alpha = 'none', size = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text.x = ggplot2::element_text(face = 'bold', size = 7, angle = 270, hjust = 0, vjust = 0.5),
                 legend.position = 'none',
                 strip.background = ggplot2::element_rect(fill = 'white'),
                 strip.text.y.right = ggplot2::element_text(face = 'bold', size = 9),
                 strip.text.x.top = ggplot2::element_text(face = 'bold', size = 10)) + 
  ggplot2::scale_x_date(date_breaks = 'weeks', date_labels = '%b %d') +
  ggplot2::facet_grid(
    
    rows = vars(metric), 
    
    cols = vars(factor(club, levels = c('D', '3W', '4', '5',
                                        '6', '7', '8', '9',
                                        'PW', 'GW', 'SW', 'LW', 'P'))),
                      scales = 'free')
```

#### Full Stroke Average

```{r PlotStrokeQualityMetricAverages, include = T, message = F, warning = F, eval = T,fig.width=11}
full_stroke_quality_avg |> 
  dplyr::ungroup() %>%
  dplyr::mutate(dplyr::across(dplyr::everything(), ~as.character(.x))) |> 
  tidyr::pivot_longer(cols = c(dplyr::contains("rd")), names_to = 'metric', values_to = 'vals') |> 
  dplyr::mutate(metric = dplyr::case_when(grepl(metric, pattern = 'target') ~ 'avg. target distance',
                                          grepl(metric, pattern = 'traveled') ~ 'avg. shot distance',
                                          grepl(metric, pattern = 'diff') ~ 'avg.\ntarget dist. - shot dist.',
                                          # grepl(metric, pattern = 'accuracy') ~ 'avg\naccuracy',
                                          grepl(metric, pattern = 'strokes') ~ 'n strokes',
                                          grepl(metric, pattern = 'dir') ~ 'strokes w/club\nin round\nby direction',
                                          grepl(metric, pattern = 'acc') ~ '% accuracy')) |> 
  dplyr::filter(!grepl(metric, pattern = 'strokes')) |>
  dplyr::mutate(date = lubridate::as_date(date),
                club = as.character(club),
                vals = as.numeric(vals)
                ) |> 
  ggplot2::ggplot(aes(x = date, y = vals, group = metric, color = club, fill = club)) +
  ggplot2::geom_point(alpha = 0.4, size = 3) +
  ggplot2::geom_line(alpha = 0.4, size = 2) +
  ggplot2::geom_smooth(method = 'lm', se = F) +
  ggplot2::labs(title = 'Full Stroke Averages by Club', x = 'date', y = 'value (yards or units)', fill = 'club') +
  ggplot2::guides(alpha = 'none', size = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(title = ggplot2::element_text(face = 'bold', size = 12),
                 axis.title = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text = ggplot2::element_text(face = 'bold', size = 10),
                 axis.text.x = ggplot2::element_text(face = 'bold', size = 7, angle = 270, hjust = 0, vjust = 0.5),
                 legend.position = 'none',
                 strip.background = ggplot2::element_rect(fill = 'white'),
                 strip.text.y.right = ggplot2::element_text(face = 'bold', size = 9),
                 strip.text.x.top = ggplot2::element_text(face = 'bold', size = 10)) + 
  ggplot2::scale_x_date(date_breaks = 'weeks', date_labels = '%b %d') +
  ggplot2::facet_grid(
    
    rows = vars(metric), 
    
    cols = vars(factor(club, levels = c('D', '3W', '4', '5',
                                        '6', '7', '8', '9',
                                        'PW', 'GW', 'SW', 'LW', 'P'))),
                      scales = 'free')
```

### Main Metrics

```{r PlotMainMetrics, include = T, message = F, warning = F, eval = T, fig.height=12, fig.width=10}
scores_sum |> 
  dplyr::mutate(course_rating = dplyr::case_when(grepl(date_course, pattern = 'Sewailo') ~ 68.9, TRUE ~ course_rating)) |> 
  tidyr::pivot_longer(cols = c(`Handicap Index`, `Gross Score`, `Net Score`,
                               `doubles+`, bogies, pars, birdies, chips, putts,
                               `UpDown%`,`Avg GIR putts`, `GIR%`, `Par 3 GIRs`,
                               `Iron FIR%`, `Driver FIR%`), names_to = 'metric', values_to = 'value', values_drop_na = F) |> 
  ggplot2::ggplot(aes(x = date_course, y = value, group = metric, color = metric, fill = metric)) +
  ggplot2::geom_point(aes(x = date, y = value, size = 4, alpha = 0.1), na.rm = T) +
  ggplot2::geom_line(aes(x = date, y = value, size = 1, alpha = 0.1), na.rm = T) +
  ggplot2::geom_smooth(aes(x = date, y = value), alpha = 0.3, method = 'lm') +
  ggplot2::labs(title = paste0('Performance Over Time\n',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::last() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character(),
                               ' - ',
                               scores |> 
                                 dplyr::distinct(date) |> 
                                 dplyr::first() |> 
                                 unlist() %>% lubridate::as_date(.) |> 
                                 as.character()),
                x = 'date',
                y = 'metric',
                color = 'metric', fill = 'metric') +
  ggplot2::guides(alpha = 'none', size = 'none') +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = 'none',
                 panel.grid.minor = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(face = 'bold'),
                 axis.text.y = ggplot2::element_text(face = 'bold'),
                 axis.text.x = ggplot2::element_text(face = 'bold', angle = 270, hjust = 0, vjust = 0.5),
                 title = ggplot2::element_text(face = 'bold'),
                 strip.text.x.top = ggplot2::element_text(face = 'bold'),
                 strip.background = ggplot2::element_rect(color = 'black',
                                                          fill = 'white')) +
  ggplot2::scale_x_date(date_breaks = '1 month', date_labels = '%b') +
  ggplot2::facet_wrap(~factor(metric,
                      levels = c('Handicap Index', 'Gross Score', 'Net Score',
                                 'doubles+', 'bogies', 'pars', 'birdies',
                                 'chips', 'putts', 'UpDown%', 'Avg GIR putts',
                                 'GIR%', 'Par 3 GIRs', 'Iron FIR%', 'Driver FIR%')),
                      scales = 'free',
                      ncol = 4)
```

